---
title: "GLMformat"
author: "Sarah Bolinger"
date: "2023-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Nest Fate Misclassification GLM

Now, the data for the GLM. First, we will select only the cameras with
nests, because the response variable is fate misclassification
(difference between camera and field fate).

We then reduce back to one row per nest by condensing the observation
history to one cell,

```{r}
# filename <- "model_data/all_nest_data_GLM_0823_1555.csv"
# ndGLM <- read_csv()

nestData <- read_csv("nest_data_cleaned_0906_0949_.csv",
                     col_types = cols(.default="c"))
now = format(Sys.time(), "%m%d_%H%M_")
```


```{r}
ndGLM <- nestData %>% 
  filter(camera == TRUE) %>% 
  group_by(nest, site, species) %>%   
  select(nest, site, species, cov_5m, fate_date, nest_age, obs_int, i, j, k, final_fate, cam_fate, status, year )%>%
  summarize(status = list(status), 
            across(where(is.integer), last),
            across(where(is.numeric), last),
            across(where(is.character), first)
  ) %>%
  mutate_if(is.list, ~paste(unlist(.), collapse = '|'))

table(ndGLM$species)
table(ndGLM$site)
table(ndGLM$year)
 
```

```{r}
howMis <- function(fate, cfate){
  case_when(
    #fate == 0                  & cfate %in% c(2,3,4,5,6)     ~ "F", 
    #fate == 0            & cfate == 1           ~ "M", # fail-unkn -> hatch
    #fate == 0            & cfate %in% c(1:6)    ~ "M", # fail-unkn -> other
    #fate == 7            & cfate %in% c(0:6)    ~ "N", # unknown -> other
    
    fate %in% c(0:6)  & cfate != fate        ~ "M", # fate    -> other 
    fate %in% c(7,8)  & cfate %in% c(0:6)    ~ "N", # unknown -> other
    fate %in% c(0:6)  & cfate == 7           ~ "U"  # unknown cam fate
  )
}
```

```{r}
ndGLM <- ndGLM %>% 
  mutate(hatchfail = case_when(
    final_fate %in% c(0, 2:6) ~ 0, # fail
    final_fate == 1           ~ 1, # hatch
    final_fate == 7           ~ 7,
    final_fate == 8           ~ 7,
    final_fate == NA          ~ 7 # MAKE SURE all of these are coding correctly
  ),
  c_hatchfail = case_when(
    cam_fate %in% c(0, 2:6) ~ 0,
    cam_fate == 1           ~ 1,
    cam_fate == 7           ~ 7,  # hopefully not many/any of either of these
    #cam_fate == NA          ~ 7   # this one doesn't work - oh duh
    is.na(cam_fate)         ~ 7
    # remove cam_fate == 7?
  )) %>%
  mutate(HF_mis = case_when(
    c_hatchfail == 7 | hatchfail == 7 ~NA,
    c_hatchfail == hatchfail ~ 0, # nest wasn't misclassified
    c_hatchfail != hatchfail ~ 1  # nest was misclassified
  )) %>%
  mutate(HF_mis = ifelse(c_hatchfail == 7, NA, HF_mis),
         HF     = case_when(
           hatchfail == 0 & c_hatchfail == 1 ~ 101,
           hatchfail == 1 & c_hatchfail == 0 ~ 110
         )) # camera H/F unknown
  
  
```

Failure misclassification
so are we talking about nests that *actually failed*? (probably)
not nests that were marked as failed in the field

or has to be both? because reclassifying from 0 to 1 OR 1 to 0 is covered in the first
analysis.

first need to verify that nest cam fate == some type of failure
(AND field fate == fail, too?)
then, was nest misclassified or not

```{r}
# ndGLM_f <- ndGLM[ndGLM$cam_fate != 1,]
# 

fail_mis <- function(fate, cfate){
  
  
  
}

ndGLM <- ndGLM |> mutate(
  
  f_class = case_when(
    
    c_hatchfail == 1 ~ NA,
    c_hatchfail == 0
    
  )
  
)

```

```{r}
ndGLM <- ndGLM %>% 
