---
title: "RMark-ch1"
author: "Sarah Bolinger"
date: "2023-09-07"
output: html_document
---

This script takes the cleaned nest data and converts it to a form
that can be used with RMark. 

It then runs the RMark models on the following data subsets:

- field-only 
    - all
    - CONI 
    - LETE
    
- camera-assisted
    - all 
    - CONI
    - LETE
- 

```{r}
remove(list=ls())
# assign('last.warning', NULL, envir=baseenv())

library(RMark)
library(tidyverse)
```

Not sure how I got to these 243 nests, especially because if you remove nests without
an age from this group, you lose most of them. Whereas with the other group, it was over 
300 even after removing no-age nests...

```{r}
#filename = 'MARKdataRUTH2019-withcam.csv'         # run analysis including cam nests
#filename = 'MARKdataRUTH2019-nocam.csv'          # run analysis excluding cam nests
# 
# filename  = "model_data/MARK_data_cam_830_954.csv"
# filename2  = "model_data/MARK_data_field_830_954.csv" # how did I narrow it to these 243?
# # # 
# filename  = "model_data/MARK_data_cam_1115_1243_.csv"
# filename2  = "model_data/MARK_data_field_1115_1243_.csv"
# filename  = "model_data/MARK_data_cam_1115_1659_.csv"
# filename2  = "model_data/MARK_data_field_1115_1659_.csv"
```


```{r}
# WITHOUT COVARIATES
filename = "model_data/ruth_rmark_cam_0329_1515_.csv"
filename2 = "model_data/ruth_rmark_fld_0329_1515_.csv"
```

```{r}
filename = "model_data/ruth_rmark_cam_0329_1742_.csv"
filename2 = "model_data/ruth_rmark_fld_0329_1742_.csv"
```


<!-- NAs for k were already removed, but not for i and j -->
How is it that I got more different DSR values when field and cam datasets had
the same number of nests than when they didn't?
Why does removing unknown fate nests not change DSR more?
I guess partly because I'm using a bigger sample here - I didn't remove the nests with
no age or whatever?
But if I ever want to use nest age as a covariate, need to remove those
Even then, difference gets even smaller?

For this analysis, should I use only the nests mentioned in the manuscript?

Also getting lots of warnings that i, j, k are in wrong order

Camera-assisted fates:

```{r}
dataNestC = read.csv(filename)
# dataNestC <- dataNestC %>% mutate(i = !is.na(i),
#                                   j = !is.na(j),
#                                   k = !is.na(k))
# dataNestC = dataNestC[,-1]

# table(dataNestC$i)
# table(dataNestC$j)
# table(dataNestC$k)
```

What is this chunk doing?
Seems to be adding back in the nests that have NAs?

```{r}
# dataU <- read.csv("model_data/unk.csv")
# dataNestC <- rbind(dataNestC, dataU)
```

This filtering was already done in the other script..

```{r}
# dataNestC <- dataNestC %>% 
#   # filter(site %in% c("RUTW", "RUTE")) %>%
#   filter(species %in% c("CONI", "LETE"))
#   # filter(!is.na(nest_age))
```

Field-based fates:

```{r}
dataNestF = read.csv(filename2)
# dataNestF <- dataNestF %>% mutate(i = !is.na(i), # this gives Boolean output
#                                   j = !is.na(j),
#                                   k = !is.na(k))
# table(dataNestF$i)
# table(dataNestF$j)
# table(dataNestF$k)
```


```{r}
dataNestF <- dataNestF %>% 
  # filter(site %in% c("RUTW", "RUTE")) %>%
  filter(species %in% c("CONI", "LETE")) 
  # filter(!is.na(nest_age))
# nocc     = dataNest$nocc
```

can look at DSR AIC in a similar model 
**Subtract 9 because they start at 10 for some reason**
```{r}

# s = 9
# dataNestC <- dataNestC %>% mutate(i = i-s,
#                                   j = j-s,
#                                   k = k-s)
# 
# dataNestF <- dataNestF %>% mutate(i = i-s,
#                                   j = j-s,
#                                   k = k-s)
# table(dataNestC$i)
# table(dataNestC$k)
# table(dataNestF$i)
# table(dataNestF$k)
```

REMOVE eval=FALSE to run the following code IF USING NEST AGE

```{r eval=FALSE, include=FALSE}
dataNestF <- dataNestF |>
  filter(!is.na(nest_age))

dataNestC <- dataNestC |>
  filter(!is.na(nest_age))
```

All nests with assigned fate, both species:

Note that sample size is larger when camera-assisted fates were incorporated;
that dataset has more assigned fates and therefore more usable nests

```{r}
null_dataC <- dataNestC %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate,
         # Freq        = 1) %>%
         Freq        = freq,
         AgeDay1     = nest_age - k 
         #AgeDay1     = nest_age - (k-i)
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
  #        Freq        = freq) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

# LETE = dataNestC$species=="LETE"
# CONI = dataNestC$species=="CONI"
# null_LETEc <- null_dataC %>% filter(species=="LETE")
# null_LETEc <- null_dataC[null_dataC$]
# null_CONIc <- null_dataC %>% filter(species=="CONI")

null_dataF <- dataNestF %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate,
         # Freq        = 1) %>%
         Freq        = freq,
         AgeDay1     = nest_age - k 
         # AgeDay1     = nest_age - (k-i) # age when assigned minus days observed
  # )
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
         # ) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

# nullLETEf <- null_dataF %>% filter(species=="LETE")
# # nullCONIf <- null_dataF %>% filter(species=="CONI")
```

Just for Least Terns:

```{r}
null_LETEc <- dataNestC %>% 
  filter(species=="LETE") %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate, 
         Freq        = freq,
         AgeDay1     = nest_age - k
         # AgeDay1     = nest_age - (k-i) # age when assigned minus days observed
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
  # )
         
         # Freq        = 1) %>%
  #        Freq        = freq) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

null_LETEf <- dataNestF %>% 
  filter(species=="LETE") %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate, 
         Freq        = freq,
         AgeDay1     = nest_age - k
         # AgeDay1     = nest_age - (k-i) # age when assigned minus days observed
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
  # )
         # Freq        = 1) %>%
  #        Freq        = freq) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

# how to find nocc? max(season_day)?
#dat = null_data
#
## lots of other options / arguments to try out!
```

Just for Common Nighthawks:

```{r}

null_CONIf <- dataNestF %>% 
  filter(species=="CONI") %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate, 
         Freq        = freq,
         AgeDay1     = nest_age - k
         # AgeDay1     = nest_age - (k-i) # age when assigned minus days observed
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
  # )
         # Freq        = 1) %>%
  #        Freq        = freq) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

null_CONIc <- dataNestC %>% 
  filter(species=="CONI") %>%
  mutate(Name        = sprintf("/*RUTH_%s*/", nest),
         FirstFound  = i,
         LastPresent = j,
         LastChecked = k,
         Fate        = fate, 
         Freq        = freq,
         AgeDay1     = nest_age - k
         # AgeDay1     = nest_age - (k-i) # age when assigned minus days observed
  ) |>
  select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq, AgeDay1)
  # )
         # Freq        = 1) %>%
  #        Freq        = freq) %>%
  # select(Name, FirstFound, LastPresent, LastChecked, Fate, Freq)

```

To run an age-based model, need a variable with all ages *on day 1 of the season*
(most will be negative)

Set of models you can run is restricted by your PIMS

- Need an all-different PIMS (the default) to run a completely general model
     - e.g. the real parameters (survival in this case) are different for each nest
     
- Design data:
    - Can use cohort, time, and age (factors); Cohort, Time, & Age = continuous
    - model_matrix() creates the design matrix based on formula & data
    - can also extend/manipulate design data if needed
    
What is model.parameters doing?

```{r}

run_rmark_models = function(dat){
    # nocc = max(dat$LastChecked)
    # Dot = mark( dat, nocc = 129 , model='Nest', se=TRUE, prefix="rmark/RUTH",
    # Dot = mark( dat, nocc = 115 , model='Nest', se=TRUE, prefix="rmark/RUTH",
    Dot = mark( dat, model='Nest', nocc = 112 , se=TRUE, prefix="rmark/RUTH",
    # Dot = mark( dat, nocc = nocc , model='Nest', se=TRUE, prefix="rmark/RUTH",
                model.parameters=list(S=list(formula=~1)) )
    
    Age = mark(dat, model='Nest', nocc=112, se=TRUE, prefix="rmark/RUTH",
               model.parameters=list(S=list(formula=~NestAge)))
    
    Time = mark(dat, model='Nest', nocc=112, se=TRUE, prefix="rmark/RUTH", 
                model.parameters=list(S=list(formula=~Time)))
    
    # AgeTime = mark(
    #   dat, nocc=112, model='Nest', se=TRUE, prefix="rmark/RUTH",
    #   model.parameters=list(S=list(formula=~Time+NestAge))
    #   )
    
    

    return(collect.models())
}
```

I manually edited the rows that were giving warnings (dates out of order, etc)

10/2024: suddenly it's throwing an error:
"Misspecification of model or internal error in code"

Suggestion from phidot forums: break "mark()" into its component functions to 
see where the issue lies.

```{r}

prdataNestC = null_dataC |> 
  RMark::process.data( 
    # null_dataC,
     model="Nest",
     nocc=112
  )   
dd_NestC = prdataNestC |>
  RMark::make.design.data() 

mod_NestC = RMark::make.mark.model(
  data=prdataNestC,
  ddl=dd_NestC
) 


resultsNC = RMark::run.mark.model(
  mod_NestC
  )
```


```{r}
resultsNestC  = run_rmark_models(null_dataC)
resultsNestF  = run_rmark_models(null_dataF)
resultsNestLC = run_rmark_models(null_LETEc)
resultsNestLF = run_rmark_models(null_LETEf)
resultsNestCC = run_rmark_models(null_CONIc)
resultsNestCF = run_rmark_models(null_CONIf)

#resultsNestC$results
```

Save output to file

```{r}
nm <- function(x) substitute(x)
dp <- function(x) deparse(x, width.cutoff=150)
now = format(Sys.time(), "%m%d_%H%M_")

saveMARK <- function(l, numMods){
  # browser()
  # for(n in range(1:numMods)){
  mod_df <- data.frame(
    model=c(1:numMods),
    name = NA,
    aicc = NA,
    psurv = NA,
    se    = NA,
    lcl   = NA,
    ucl   = NA,
    n     = NA
    )
  for(i in 1:numMods){
    # filename = sprintf("MARKoutput_%s_%s_%s", dp(data), n, now)
    # filename = sprintf("MARKoutput_%s_%s_%s", dp(dat), n, now)
    # datName <- dp(nm(dat))
    datName <- dp(substitute(l))
    # mod     <- df$numMods
    mod             <- l[[i]]
    mod_df$name[i]  = mod$model.name
    mod_df$aicc[i]  = mod$results$AICc
    mod_df$psurv[i] = mod$results$real$estimate
    mod_df$se[i]    = mod$results$real$se
    mod_df$lcl[i]   = mod$results$real$lcl
    mod_df$ucl[i]   = mod$results$real$ucl
    mod_df$n[i]     = nrow(mod$data$data)
    
    # filename = sprintf("MARKoutput_%s_%s_%s.csv", datName, n, now)
    # # write.csv(dat$numMods[n], filename)
    # write.csv(mod, filename)
  filename = sprintf("rmark/MARKoutput_%s_%s.csv", datName, now)
  # write.csv(dat$numMods[n], filename)
  write.csv(mod_df, filename)
  }
  return(mod_df)
}
```

```{r}
now = format(Sys.time(), "%m%d_%H%M_")

saveMARK(resultsNestC, 4)
saveMARK(resultsNestLC, 4)
saveMARK(resultsNestCC, 4)
saveMARK(resultsNestF, 4)
saveMARK(resultsNestLF, 4)
saveMARK(resultsNestCF, 4)
```

```{r}
d.C = resultsNestC$Dot$results$real[, 1:4] 
d.F = resultsNestF$Dot$results$real[,1:4]
d.LC = resultsNestLC$Dot$results$real[,1:4]
d.LF = resultsNestLF$Dot$results$real[,1:4]
d.CC = resultsNestCC$Dot$results$real[,1:4]
d.CF = resultsNestCF$Dot$results$real[,1:4]


# s.dot = cbind(s.d[rep(seq_len(nrow(s.d)), each = 8), ],
              # Week = 1:8, 
              # Model = "constant")
# 
# s.t = cbind(resultsNestC$S.time$results$real[, 1:4],
#             Week = 1:8, 
#             Model = "time-varying")
# 
# s.T = cbind(bduck.results$S.TIME$results$real[, 1:4],
#             Week = 1:8, 
#             Model = "Time trend")
# 
# s.temp = cbind(bduck.results$S.temp$results$real[, 1:4],
#                Week = 1:8,
#                Model = "temperature")

# store all the estimates in a data frame
# surv.ests = rbind(s.dot, s.t, s.T, s.temp)
surv.ests = rbind(d.C, d.F)
surv.estsL = rbind(d.LC, d.LF)
surv.estsC = rbind(d.CC, d.CF)
model <- c("cam", "field")
surv.ests = cbind(model, surv.ests)
surv.estsL = cbind(model, surv.estsL)
surv.estsC = cbind(model, surv.estsC)

surv <- rbind(surv.ests, surv.estsC, surv.estsL)
surv$species <- c("all", "all", "CONI", "CONI", "LETE", "LETE")
# surv.ests = cbind(model, surv.ests, surv.estsC, surv.estsL)
# names(surv.ests) <- model
```


```{r}
# ggplot(surv, aes(x=model, y=estimate, color=species)) + 
ggplot(surv, aes(x=species, y=estimate, color=model)) + 
  # geom_boxplot()
  # geom_point() +
  geom_point(size=3, position=position_dodge(width=0.5)) +
  # geom_jitter() +
  # geom_errorbar(aes(ymin=lcl, ymax=ucl))
  geom_errorbar(aes(ymin=lcl, ymax=ucl),
                width=0.1,
                position=position_dodge(width=0.5))
# ggplot(surv.ests, aes(x=model, y=estimate)) + 
  # geom_boxplot()
  # geom_point() +
  # geom_errorbar(aes(ymin=lcl, ymax=ucl))

# Make plot
# The errorbars overlapped, so use position_dodge to move them horizontally
# pd <- position_dodge(0.4) 
# 
# ggplot(surv.ests, aes(x = Week, y = estimate, color = Model)) +
#   geom_errorbar(aes(ymin = lcl, ymax = ucl), 
#                 width = 0.1, 
#                 position = pd) + 
#   geom_line(position = pd) +
#   geom_point(position = pd) +
#   scale_y_continuous("Weekly Survival Estimates", 
#                      limits = c(0, 1), 
#                      breaks = seq(0, 1, by = 0.1)) + 
#   theme_bw() + # black and white theme
#   theme(legend.justification = c(1, 0.1),
#           legend.position = c(0.9, 0.1)) # Position legend in lower left
```

Extract DSR values with ucl and lcl

```{r}
# CONI
# survAC = 0.7
survAC = 0.8
# survJC = 0.4
survJC = 0.5
estCC = resultsNestCC$Dot$results$real[,1:4] 
estCF = resultsNestCF$Dot$results$real[,1:4] 
perCC = estCC ^ 16
perCF = estCF ^ 16

#LETE
survAL = 0.8
survJL = 0.5
estLC = resultsNestLC$Dot$results$real[,1:4]
estLF = resultsNestLF$Dot$results$real[,1:4]
perLC = estLC ^ 20
perLF = estLF ^ 20
```


```{r}
minBP = 0.6
# maxBP = 0.9
maxBP = 1.3
bp   = seq(minBP, maxBP, 0.05)

valsCC <- numeric(length(bp))
valsCF <- numeric(length(bp))
valsLC <- numeric(length(bp))
valsLF <- numeric(length(bp))

lambda <- function(survA, survJ, dsr_list, bp, vals, inc){
  # browser()
  dsr = dsr_list[1,1]
  psr = dsr ^ inc
  for(b in 1:length(bp)){
    # fec = (dsr*(bp[b]*(2-dsr)))/2
    fec = (psr*(bp[b]*(2-psr)))/2
    vals[b] = survA + (survJ * fec)
  }
  return(vals)
}
```


```{r}
bp2 = 0.5

lambda <- function(survA, survJ, dsr, bp, inc){
  psr = dsr ^ inc
  cat(psr)
  # fec = (psr*(bp*(2-psr)))/2
  fec = (psr*(bp*(2-psr)))/2
  val = survA + (survJ * fec)
}

# fec <- function(dsr, bp){
#   (dsr*(bp*(2-dsr)))/2
# }
# 
# for(b in 1:length(bp)){
#   f         = fec()
#   vals[[b]] = survA + survJ * f
# }
```


```{r}
CONI_c <- lambda(survAC, survJC, estCC, bp, valsCC, 16)
CONI_f <- lambda(survAC, survJC, estCF, bp, valsCF, 16)
# CONI_l <- rbind(bp, CONI_c, CONI_f)
# CONI_c <- lambda(survAC, survJC, estCC$estimate, bp, 16)
# CONI_f <- lambda(survAC, survJC, estCF$estimate, bp, 16)
names <- c("bp", "camera", "field", "species")
CONI_l <- as.data.frame(cbind(bp, CONI_c, CONI_f))
CONI_l$species = "CONI"
names(CONI_l) <- names
# CONI_l <- CONI_l %>% pivot_longer(cols=c(CONI_c, CONI_f),
CONI_l <- CONI_l %>% pivot_longer(cols=c(camera, field),
                                  names_to="CF",
                                  values_to="lambda")

# ggplot(CONI_l, aes(x=bp, y=lambda)) +
#   geom_point(aes(shape=CF))
```


```{r}

LETE_c <- lambda(survAL, survJL, estLC, bp, valsLC, 20)
LETE_f <- lambda(survAL, survJL, estLF, bp, valsLF, 20)
# CONI_f <- lambda(survAC, survJC, estCF, bp, valsCF)
# LETE_c <- lambda(survAL, survJL, estLC$estimate, bp, 19)
# LETE_f <- lambda(survAL, survJL, estLF$estimate, bp, 19)
LETE_l <- as.data.frame(cbind(bp, LETE_c, LETE_f))
LETE_l$species = "LETE"
names(LETE_l) <- names
# LETE_l <- LETE_l %>% pivot_longer(cols=c(LETE_c, LETE_f),
LETE_l <- LETE_l %>% pivot_longer(cols=c(camera,field),
                                  names_to="CF",
                                  values_to="lambda")
```

```{r}
lambda_val <- rbind(LETE_l, CONI_l)

ggplot(lambda_val, aes(x=bp, y=lambda)) +
  geom_point(aes(shape=CF, color=species)) +
  xlab("offspring per pair")
  
```



```{r}
# Lplot <- function(Ldata, nests){
#   ggplot(Ldata, aes(x=bp, y=))
# }
```







