---
title: "compare"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: html_document
---


Maybe go back and check the nest ages that I added and see if any are spurious

### import the old data

```{r echo=TRUE}
# fn2 <- paste0(homeDir,"nest_data/nest_data_cleaned_0605_1753_.csv")
# fn2 <- paste0(homeDir,"nest_data/nest_data_cleaned_0227_1740_.csv")
fn2 <- paste0(homeDir,"nest_data/grouped_0805_1225_ed_20250813_0132.csv")
# fn2 <- paste0(homeDir,"nest_data/nestdata_clean_1018_1506_.csv") # this one doesn't have camera variable!
nData2 <- read_csv(fn2)[-c(1)]
# nData2 <- read_csv(fn2)

if(old_data){
  cat("using old data")
  nData2$fdate <- nData2$k
  ff(nData2) # add a field fate column
} else {
  nData2$fdate <- nData2$final_obs_date
  nData2$final_fate <- nData2$final_fate2
  # nData$field_fate <- nData$field_fate2
  nData2$field_fate <- nData2$field_fate3
  if(feb==TRUE){
    cat("using february data")
    nData2$obs_int <- nData2$final_obs_int_feb
    nData2$nest_age <- nData2$nest_age_feb
    nData2$cam_fate   <- nData2$cam_fate_feb
  } else  {
    cat("using regular data")
    # nData$obs_int <- nData$final_obs_int
    nData2$obs_int <- nData2$final_obs_int2
    nData2$nest_age <- nData2$nest_age1 # nest age based on actual obs date
    # nData$nest_age <- nData$nest_age2 # nest age based on hatch date
    nData2$cam_fate   <- nData2$cam_fate2
  }
}
# if(feb==TRUE){
#   nData2$final_obs_date <- nData2$k
#   nData2$fdate          <- nData2$k
# }
names(nData2)
```

### Add a "field_fate" column, make U-H into H the way it used to be. Also, filter the data and add the predictors.

filter_dat assumes ungrouped data by default.

```{r echo=TRUE}
if(old_data){
nd_2 <- nData2 %>%
    mutate(field_fate = final_fate) %>%
    mutate(final_fate = coalesce(cam_fate, field_fate )) %>%
    filter(nest!=20365) %>%
    filter_dat(sites = sites_sel, spp = spp_sel, cam_vect = cam_str, debug = TRUE) %>%
    mutate(fate=ifelse(field_fate=="U-H", 1, fate))
  table(nd_2$fate)
  # ndGLM_test <- as.data.frame(add_vars(nd_2, UHisH=UHisH, UFisF=UFisF, debug=T))
  ndGLM_test <- as.data.frame(add_vars(nd_2,  debug=T))
  ndGLM_test <- ndGLM_test %>% select(nest, status, species, field_fate, cam_fate, final_fate, fate_date, fdate, nest_age, obs_int, how_mis, HF_mis, misclass, is_u, hatchfail, c_hatchfail, fate, cfate)
}else{
  nd_2 <- nData2 %>%
    filter(nest!=20365) %>%
    filter_dat1(sites = sites_sel, spp = spp_sel, cam_vect = cam_str, grouped=TRUE, debug = TRUE)
  
  ndGLM_test<- as.data.frame(add_vars(nd_2, debug=T)) 
  ndGLM_test <- ndGLM_test %>% select(nest,species, field_fate, cam_fate, final_fate, fdate, nest_age, obs_int, how_mis, HF_mis, misclass, is_u, hatchfail, c_hatchfail, fate, cfate)
}
```

### Remove rows missing camera fate; visualize the data before and after.

```{r echo=TRUE}

# ```{r echo=TRUE}
# 
cat("BEFORE REMOVING CAM FATE NA:\n\n")
print_vars(ndGLM_test)
ndGLM_red2 <- ndGLM_test[!is.na(ndGLM_test$cam_fate),]
ndGLM_red2 <- ndGLM_red2[ndGLM_red2$cam_fate!="U",]
ndGLM_red2$nest[is.na(ndGLM_red2$misclass)] 
cat("AFTER REMOVING CAM FATE NA:\n\n")
ndGLM_miss2 <- dat_miss(ndGLM_red2)
print_vars(ndGLM_red2)


ndGLM_red2_2 <- ndGLM_red2 %>%
  set_var_types() %>%
  # refactor(num_fate=4) %>%
  # refactor(num_fate=6) %>%
  mutate(mclass = misclass == 1,
         isu    = is_u == 1) %>%
  mutate(across(c(isu, mclass), as.factor))

print_vars(ndGLM_red2_2)
```

### Reduce the number of fate categories by combining human- and cattle-related failure.

```{r echo=TRUE}

nfate=6
ndGLM_2 <- ndGLM_red2_2 %>%
  refactor(num_fate=nfate) 
# levels(ndGLM6$cam_fate)

ndGLM_2_cc <- ndGLM_2 %>% # I don't know why this isn't working
  remove_na(allNA = ndGLM_miss2) %>%
  mutate(obs_int = ifelse(nest==20256,6,obs_int))
```

### Compare before removing all NAs (just cam fate NA removed):

Moved this earlier so cam_fate shows up as strings, not numbers (after you make it into a factor)

```{r echo=TRUE}
# summary(arsenal::comparedf(ndGLM_, ndGLM_2))
# dfDiffSum <- summary(arsenal::comparedf(ndGLM_, ndGLM_2, by="nest"))
# 
# nData = ndGLM_red
# nData2 = ndGLM_red2
datNames <- c("ndGLM_red", "ndGLM_red2")
d1 <- get(datNames[1])
d2 <- get(datNames[2])
byVar <- "nest"

# dfDiffSum <- summary(arsenal::comparedf(ndGLM_red, ndGLM_red2, by="nest"))
dfDiffSum <- summary(arsenal::comparedf(d1, d2, by=byVar))
dfDiffSum
print(dfDiffSum$obs.table)
# write.csv(dfDiffSum$obs.table, "output/df-diff-obs.csv")
now = format(Sys.time(), "_%m%d_%H%M_")
write.csv(dfDiffSum$obs.table, paste0(
  "output/diff-obs_",datNames[1],"_",datNames[2],"_by",byVar,"_", now, ".csv"
  ))
dfDiffs   <- arsenal::diffs(dfDiffSum)
# dfDiffs
write.csv(dfDiffs, paste0(
  "output/df-diff_",datNames[1],"_",datNames[2],"_by", byVar,"_", now, ".csv"
  ))

diffVars  <- dfDiffSum$vars.ns.table %>%
  unnest(cols=class)
write.csv(diffVars, paste0(
  "output/diff-vars_",datNames[1],"_",datNames[2],"_by", byVar, now, ".csv"
  ))
```


```{r echo=TRUE}
datNames <- c("ndGLM_cc", "ndGLM_feb_cc")
d1 <- get(datNames[1])
d2 <- get(datNames[2])
byVar <- "nest"
# dfDiffSummCC <- summary(arsenal::comparedf(ndGLM_cc, ndGLM_feb_cc, by="nest"))
dfDiffSummCC <- summary(arsenal::comparedf(d1, d2, by="nest"))
# write.csv(dfDiffSummCC$obs.table, "df-diff-obs-cc.csv")
write.csv(dfDiffSummCC$obs.table, paste0(
  "output/diff-obs-cc_",datNames[1],"_",datNames[2],"_by",byVar,"_", now, ".csv"
  ))

dfDiffsCC   <- arsenal::diffs(dfDiffSummCC)
# dfDiffs
# write.csv(dfDiffsCC, "output/df_differences_cc.csv")
write.csv(dfDiffsCC$obs.table, paste0(
  "output/df-diff-cc_",datNames[1],"_",datNames[2],"_by",byVar,"_", now, ".csv"
  ))

diffVarsCC  <- dfDiffSummCC$vars.ns.table %>%
  unnest(cols=class)
write.csv(diffVarsCC, paste0(
  "output/diff-vars-cc_",datNames[1],"_",datNames[2],"_by", byVar, now, ".csv"
  ))
```
