---
title: "Nest fate exact LR"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: html_document
---


#### Exact logistic regression

For the model that won't converge using brglm2 (with either brglmFit or jeffrey's)
Still haven't figured out the error from logistf

Interaction term needs to be written out to match what is in "interest"

Response variable is binomial, so must be expressed as # successes/# trials for each row of the dataset.

Meant to be run as a child document within another script (like fate_GLM.Rmd)

```{r eval=FALSE, include=FALSE}
# exactDat <- ndGLM_unscl_cc %>%
exactDat <- ndGLM_cc %>%
  # mutate(across(c(is_u, HF_mis, species, cam_fate)), as.integer()) %>%
  mutate(across(c(is_u, HF_mis, species, cam_fate), as.numeric)) %>%
  group_by(species, cam_fate, nest_age, fdate, obs_int) %>%
  mutate(n=n()) %>% 
  ungroup() %>%
  distinct()
exactFit <- elrm::elrm(formula = is_u/n ~ species + cam_fate + species:cam_fate + nest_age + fdate + obs_int,
     interest = ~species:cam_fate, 
     iter = 50000,
     dataset = exactDat)

exactFit2 <- elrm::elrm(formula = HF_mis/n ~ species + cam_fate + species:cam_fate + nest_age + fdate + obs_int,
     interest = ~species:cam_fate, 
     iter = 50000,
     dataset = exactDat)

now = format(Sys.time(), "_%m%d_%H%M_")
saveRDS(exactFit, file=paste0("exactFit1",now".rds"))
saveRDS(exactFit2, file=paste0("exactFit2",now".rds"))
```


```{r eval=FALSE, include=FALSE}
summary(exactFit)
summary(exactFit2)
```


```{r eval=FALSE, include=FALSE}
# ex <- readRDS("exactFit1.rds")
# ex2 <- readRDS("exactFit2.rds")
# ex <- readRDS("exactFit1_old.rds")
# ex2 <- readRDS("exactFit2_old.rds")
suff1 <- "_09aug"
suff2 <- "_"
fn1 <- paste0("exactFit1",suff1,".rds")
fn2 <- paste0("exactFit2",suff2,".rds")
ex1 <- readRDS(fn1)
ex2 <- readRDS(fn2)

summary(ex)
summary(ex2)
```
