---
title: "Untitled"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)
```
---
title: "fate_GLM_imputation"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)
# library(marginaleffects)
library(tidyverse)
library(brglm2) # the line below SHOULD mean I don't have to load this, but it's not working
```

## Run all of these once:

### Functions

```{r, warning=FALSE}
###  to perform the multiple imputations ###############################################

# impRes <- impDat %>%
#   select(nest, nest_age, obs_int, cam_fate, fdate, species, HF_mis, misclass, is_u) %>%
#   # runImpMods(.,modList=modList,resp="is_u")
#   runImpMods(.,modList=modList,regMethod = impMet,resp=resp, pool=FALSE, impute=FALSE)
# summary(impRes)
# impRes

# all of this is what is inside the function
# impDat1 is the result of get(datNameImp)

imputeDat <- function(impDat1, m = 10, return = "complete"){
  
  # impDat1 <- get(datNameImp)
  impDat  <- mice::mice(impDat1, seed=613, m=m, printFlag=FALSE)
  impDat2 <- mice::complete(impDat, "all") # generate a list of all the completed datasets
  
  print(plot(impDat))
  print(attributes(impDat))
  
  if(return=="complete") return(impDat2) else return(impDat)
}
```

```{r, warning=FALSE}
# fit the models using each of the m datasets
impFit <- function(impDat, modList){
  
    impMod <- vector(mode="list", length=length(modList))
    
    for (m in seq_along(modList)){
      impMod[[m]] = with(impDat, glm(as.formula(
        # paste0(resp, modList[[m]])), family=fam, method=brglm2::brglm_fit))
        
        # how come regMet works in the nestGLM package but not here??
        paste0(resp, modList[[m]])), family=fam, method = regMet, 
        # paste0(resp, modList[[m]])), family=fam, method =impMet,
        control=brglmControl(maxit=iter)
      ))
    }
    
    return(impMod)
    
}

# pool the results
poolImp <- function(impMod, modList){
  impModPool <- vector(mode="list", length=length(modList))
  
  for(m in seq_along(modList)){
    impModPool[[m]] = mice::pool(impMod[[m]])
    summary(impModPool[[m]])
    # impModPool[[m]] %>%
    #   gt::gt() # was this new? not working 12 aug 25
  }
  return(impModPool)
}
```

```{r}
# dat <- impDat
# modnum=top_num
# plot_type = "pred"
# # if(grepl("*", modList[top_num], fixed=TRUE)){
# vars = c(intVar1, intVar2)
# y_lab="e"
# x_lab="jjkjk"
# grid1 <- intGridAge
```

```{r}
# create the interaction plots
grpColor <- c(LETE="#AA4499", CONI="#44AA99")
intPlot <- function(dat, 
                    modnum, 
                    plot_type = "pred", 
                    vars=c("species", "nest_age"),
                    y_lab = "Predicted probability of\n misclassification",
                    x_lab = "Nest age - centered (days)",
                    # grid=intGrid1 # probably shouldn't have the same name as a function?
                    # grid1=intGrid1 # probably shouldn't have the same name as a function?
                    grid1
                    ){
  
    model   <- with(dat,
                    glm(as.formula(paste0(resp, modList[[modnum]])),
                    family=binomial,
                    method=regMet
                    ))
    
    intSlope <- marginaleffects::slopes(model,
                                        variables=vars,
                      # variables=c("species", "obs_int"),
                      newdata=grid1)
    #  from the documentation: 
    #  Warning: Slopes and elasticities can only be calculated for continuous numeric variables. The slopes() functions will automatically revert to comparisons() for binary or categorical variables.
    #  
    #  Why are all the predictions only a few values?
    intPred <- marginaleffects::predictions(model,
                                            newdata=grid1,
                                            # variables=c("species", "nest_age"))
                                            # so was this always working with these 2 variables?
                                            variables=vars
                                            )
    
    # this one gives a list as output:
    # plDat   <- ifelse(plot_type=="slope",as.data.frame(intSlope),as.data.frame(intPred))
    plDat <- intPred
    if(plot_type=="slope") plDat <- intSlope
    # the confidence intervals in this plot don't seem wide enough...
    # plDat <- case_when(plot_type == "pred" ~ intPred,
    #                    plot_type == "slope" ~ intSlope)
    # ggplot(intPred,
    mm <- sym(vars[1])
    xx <- sym(vars[2])
    colores <- c("")
    g <- ggplot(plDat,
           # aes(x=obs_int, y=estimate, ymin=conf.low, ymax=conf.high, color=species)) +
           # aes(x=as.numeric(obs_int), y=estimate, ymin=conf.low, ymax=conf.high, color=species)) +
           aes(x=!!xx, y=estimate, color=!!mm)) +
      # geom_point() +
      labs(x=x_lab, y=y_lab)+
      scale_color_manual(values=grpColor,
                         labels=c("Common\nNighthawk", "Least Tern"),
                         name="Species") +
      geom_smooth(method=NULL) +
      theme_classic() +
      theme(axis.text = element_text(size=18),
      axis.title = element_text(size=20), # can't do margins for x and y axis titles at once
      legend.text=element_text(size=16),
      legend.title=element_text(size=18),
      axis.title.y = element_text(margin=margin(r=5)),
      axis.title.x = element_text(margin=margin(t=5))) 
      # geom_ribbon(alpha=0.2) +
      # geom_line()
  }
# }
```

### Create a small set of imputations (m=10) for testing code (does not run during knitting)

Also tells R to use the smaller set for the other functions

```{r eval=FALSE, include=FALSE, warning=FALSE}
# impute, without completing the datasets so you can use the fit command?
impDat_small <- imputeDat( impDat1 = imppDat, return= "") # default m value is 10
smallFit <- impFit(impDat_small, modList)
smallPool <- poolImp(smallFit, modList)
# Error in `brglm2::brglm_fit`(x = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,  : 
#  could not find function "brglm2::brglm_fit"
#       MAYBE HELPFUL:
# pkg::name returns the value of the exported variable name in namespace pkg, whereas pkg:::name returns the value of the internal variable name. 

# impDatsmall  <- mice::mice(impDat1, seed=613, m=10, printFlag=FALSE)
# impDatsmall2 <- mice::complete(impDatsmall, "all") # generate a list of all the completed datasets
impDat <- impDat_small
impMod <- smallFit
impModPool <- smallPool
```

### Create imputed datasets (m=100)

Really only need to create the imputed data once

```{r, warning=FALSE}
imppDat <- get(datNameImp)
impDat       <- imputeDat(impDat1 = imppDat, m=100, return="")
```
## .
#########################################################################################
#########################################################################################
## Run all of these for each separate analysis:

### Settings

```{r}
# (see chunk further down)
regMet <- "brglm_fit"
# regMet  <- "brglm2:::brglm_fit"
# regMet  <- "brglm2::brglmFit"
fam     <- binomial
iter    <- 500
fVar <- "_allFates"
uVar <- "_UHisU"
if(UHisH) uVar <- "_UHisH" 
if(exists("nfate")) fVar <- paste0("_",nfate,"fates") # exists seems to be more complicated than I thought...
cat("* * * * * * * * * * * * * * * * * * * * * * * * * * * *")
cat("\n* imputation using this data:", datNameImp)
cat("\n* and this response variable:", resp)
# cat("\nand this method:", impMet)
cat("\n* and this method:", regMet)
cat("\n* * * * * * * * * * * * * * * * * * * * * * * * * * * *")
```

### Fit & pool the results

```{r, warning=FALSE}
# uses the response specified in fate_GLM1.Rmd
impMod       <- impFit(impDat = impDat, modList = modList)
impModPool   <- poolImp(impMod = impMod, modList= modList)
```

### Create the AIC table with the model fit using the imputed data

Extract the degrees of freedom, as well as the average AIC, Akaike weight, & log likelihood 
(across all imputations) for each model, and create the AIC table.

```{r}
# lapply(impRes, summary)
fname <- paste0(datNameImp,"_impAIC",quest,uVar,fVar)

# need to have fit the models in the main script for this to work (just for naming):
aicImp <- aicImpMods(impModPool = impModPool,modList = modList,mods=mods,filePrefix = fname)
# only output is the filename - can't see the R object
# now the function also saves an RDS of the imputation AIC info.
aicImpDat <- readRDS("aicImpMod.rds")
# aic <- as.data.frame(aicImpDat)
# aic <- purrr::map_df(aicImpDat, tibble::as_tibble) # deprecated function
aicTabImp <- readRDS("impAICtab.rds")
aicTabImp
knitr::include_graphics(paste0("analysis/",aicImp),
# knitr::include_graphics(aicImp, 
                        dpi=(1300/6)) # dpi setting = only thing that works
```

### Create the pooled regression table for the top model:

```{r, warning=FALSE}
# top_num <- aicTabImp$num[1]
top_num <- as.numeric(rownames(aicTabImp)[1])
# sec_top <- aicTabImp$num[2]
sec_top <- as.numeric(rownames(aicTabImp)[2])
# 
cat("top model:", modList[top_num])
intVar1 <- str_extract(string = modList[top_num],
                       pattern = "\\w+(?=\\s\\*)")

intVar2 <- str_extract(string = modList[top_num],
                       pattern = "(?<=\\*\\s)\\w+")

cat("\ninteraction variables:", intVar1, intVar2)
# secTopMod = aicTab$`_data`$`__GT_ROWNAME_PRIVATE__`[2]
cat("\n\nsecond best model:", modList[sec_top])
intVar1.2 <- str_extract(string = modList[sec_top],
                       pattern = "\\w+(?=\\s\\*)")

intVar2.2 <- str_extract(string = modList[sec_top],
                       pattern = "(?<=\\*\\s)\\w+")

cat("\ninteraction variables:", intVar1.2, intVar2.2)
cat("\ndelta AIC of second best model:", aicTabImp$deltaAIC[2])

cat("\n\ncreating regression table for top model, model number", top_num, "; \nmodel formula:", paste(modList[top_num]))
# impTab <- impModTab(impModPool = impRes,modList = modList)
```


```{r, warning=FALSE}
# this works:

# fit <- with(impDat, glm(as.formula(paste(resp1, modList[[5]])), family=binomial, method=brglm2::brglmFit)) 
# use the number of the top model to evaluate it:
fit <- with(impDat, glm(as.formula(paste(resp, modList[[top_num]])), family=binomial, method=brglm2::brglmFit)) 
# pass results to tbl_regression before pooling, and it will handle pooling + tidying:
vars=c('species', 'nest_age', 'obs_int', 'cam_fate', 'fdate')
varNames=c('SPECIES', 'NEST_AGE', 'FINAL_INTERVAL', 'TRUE_FATE', 'END_DATE')
vnames = as.list(varNames)    
names(vnames) <- vars
# tabOR <- gtsummary::tbl_regression(pool.fit, label=vnames, exponentiate=TRUE)
summ.fit <- gtsummary::tbl_regression(fit, label=vnames, exponentiate=TRUE)
summ.fit
# fn <- sprintf("_q1_reg_imp_%s_%s.rtf", datNameImp, now)
fn <- sprintf("_%s_reg_imp_%s_%s.rtf", quest, datNameImp, now)
summ.fit %>%
  gtsummary::as_gt() %>%
  gt::gtsave( filename=fn, path="analysis/" )


```


### Plot the marginal effects if there is an interaction in the top model:

For other methods I tried that didn't work, see old_code document

Or use stratification as seen here: https://www.bookdown.org/rwnahhas/RMPH/mi-mlr.html

marginaleffects package: 

- use avg_comparisons for categorical variables and get the average predicted values for each level of X; and by=M to see if the changes depend on a moderator M

When M is continuous, use the predictions() function because calculating an average for each value of a continuous variable is not practical.

#### Create the datagrid objects that marginal effects will use as "newdata" when making predictions

```{r}

# if(grepl("*", modList[top_num], fixed=TRUE)){
  
# intGridNew1 <- marginaleffects::datagrid(newdata=ndGLM_scl,
intGridAge <- marginaleffects::datagrid(newdata=ndGLM_scl,
                                         species=c("CONI", "LETE"),
                                         # nest_age= c(-15:15)) # using the centered data
                                         nest_age= seq(-15, 15, length.out=100)) # using the centered data
                                     # obs_int = c(-4:6))

intGridObs  <- marginaleffects::datagrid(newdata=ndGLM_scl,
                                          species=c("CONI", "LETE"),
                                         # obs_int = c(-4:6)) # not a lot of values - hard to 
                                                            # get a smooth curve
                                         # using 1000 values doesn't seem to help with slopes plot
                                         # and it makes intPred have 20,000 observations
                                         # obs_int = seq(from=-4, to=6, length.out=1000)) 
                                          obs_int = seq(from=-4, to=6, length.out=100)) 
                                           
# }
if(resp=="is_u"){
  yl = "Predicted probability of\nunknown field fate"
} else {
  yl = "Predicted probability of \nmisclassification"
}
# intGridNew3 <- marginaleffects::datagrid(newdata=ndGLM_scl,
#                                          species=c("CONI", "LETE"),
#                                          )

```
```{r}
# makeIntGrid <- function(xvar, mvar, newD){
#   
# }
```

#### Go ahead and plot the interactions in all models that are in the top model set:

```{r, warning=FALSE}
if(grepl("*", modList[top_num], fixed=TRUE)){ # the defaults are for this model
  # change the grid used based on which variables are in the interaction:
  if(intVar2 == "obs_int"){
    # gr = intGridObs 
    grName = "intGridObs"
    lab = "Final interval - centered (days)"
  } else {
    # gr = intGridAge
    grName = "intGridAge"
    lab = "Nest age - centered (days)"
  }

  intPlot(impDat,                             # (interaction between species & nest_age)
          # modnum=5)
          modnum=top_num,
          vars = c(intVar1, intVar2), # in this case, intVar1 should always be species
          # grid1=gr,
          grid1=get(grName),
          x_lab=lab,
          y_lab=yl)
  # ,
          # y_lab="Predicted probability of\n unknown field fate")                   
}
```


```{r, warning=FALSE}
if(grepl("*", modList[sec_top], fixed=TRUE)){
  # if("obs_int" %in% c(intVar1.2, intVar2.2)){
  if(intVar2.2 == "obs_int"){
    # gr = intGridObs
    grName = "intGridObs"
    lab = "Final interval - centered (days)"
  } else {
    # gr = intGridAge
    grName = "intGridAge"
    lab = "Nest age - centered (days)"
  }
  
  intPlot(impDat,
            # modnum=4, 
            modnum=sec_top, 
            # grid1=gr, 
            grid1=get(grName), 
            # vars=c("species", "obs_int"), 
            vars=c(intVar1.2, intVar2.2), 
            x_lab=lab,
          y_lab = yl)
}
```

