---
title: "Nest GLM"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

## Introduction

What to do with this script:

1. Choose the data to load under section 1a
2. Decide how many categories you want to use for nest fate in section 1e
3. Check the models that will be fitted in section 3

I think it makes sense to keep the filtering function in the code for now? Easier to
edit it on the fly. Also, some of the dplyr stuff gets a little dicey in a custom package. 
Specifically, lines with across and last, like this:
              across(where(is.integer), last), # now they are all chr

```{r setup, include=FALSE}
# remove(list=ls())
knitr::opts_chunk$set(echo = TRUE)

# library(AICcmodavg)
library(bbmle)
library(brglm2) # penalized logistic regression
# library(car)
# library(detectseparation)
# library(elrm)
library(gt)
library(gtsummary)
# library(howManyImputations)
# library(insight) # to get the df for the imputed models
# library(lattice) # for some imputation operations
# library(logistf)
# library(mice) # multiple imputation
# library(MASS)
library(nestGLM)
# library(patchwork)
library(stats)
library(tidyverse)
# library(visdat)   # visualize all data and number missing
```

## 0. SETUP

### a. Set some values

```{r set-values, echo=FALSE}
homeDir <- "C:/Users/sarah/Dropbox/nest_models/"

predictors <- c("nest_age", "obs_int", "fdate") # numeric predictors to be used
prList     <- as.list(predictors)
prLabs <-  c("Nest Age (Days)", 
             "Final Interval (Days)",
             "Day of Season")
prNames <- c("NEST_AGE", "FINAL_INTERVAL", "END_DATE")
# names(predictors) <- prLabs
names(prList) <- prNames
now = format(Sys.time(), "_%m%d_%H%M_")

# filename <- paste0(homeDir,"glm_script/import_data_", now, ".csv")
# cat("import file name:", filename)
cat("homeDir =", homeDir, "|| now =", now,"\n\npredictor variables:\n\n")
print(prList)

# now some files are saved under GLM_script and some under nest_models...

```

### b. Create functions

#### Filter function


```{r filter-function, echo=TRUE}
filter_dat1 <- function(nestData, sites=c("RUTE","RUTW"), spp=c("LETE","CONI"),
                        # cam_nest=TRUE,
                        cam_vect=c("Y","y"),  debug=FALSE, grouped=FALSE){
  # cam_str <- c("Y","y")
  # if (all_cam) cam_str <- c("Y","y","Y*")
  if (debug) cat("camera strings:", cam_vect,"\n\n")
  ndGLM <- nestData %>%

    # mutate(fdate=final_obs_date) %>%    # this is also done later?
    mutate(
      fate = case_match(field_fate,
                                   "H"   ~ 1,
                                   "F"   ~ 0,
                                   "D"   ~ 2,
                                   "S"   ~ 3,
                                   "A"   ~ 4,
                                   "Hu"  ~ 5,
                                   "Ca"  ~ 6,
                                   "U"   ~ 7,
                                   "U?"  ~ 7,
                                   "U-H" ~ 8
           ),

           cfate = case_match(cam_fate,
                                 "H"  ~ 1,
                                 "F"  ~ 0,
                                 "D"  ~ 2,
                                 "S"  ~ 3,
                                 "A"  ~ 4,
                                 "Hu" ~ 5,
                                 "Ca" ~ 6,
                                 "U"  ~ 7
           ),
           camera = ifelse(camera %in% cam_vect, TRUE, FALSE)

    ) %>%

    filter(site %in% sites) %>%
    # filter(species %in% c("CONI", "LETE")) %>%
    filter(species %in% spp) %>%
    filter(camera == TRUE)

  if(grouped==F){
    ndGLM <- ndGLM %>%
    # select(nest, site, species, cov_5m, fate_date, nest_age, obs_int, i, j, k, final_fate, fate, cam_fate, cfate, status, year )%>%
    group_by(nest)  %>%
    # dplyr::select(nest, site, species, fdate, fate_date, nest_age, obs_int, i, j, k, fate, final_fate, final_fateUH, cfate, cam_fate, status, year )%>%
    # dplyr::select(nest, site, species, fdate, fate_date, nest_age, obs_int, i, j, k, field_fate, fate, final_fate, cfate, cam_fate, status, year )%>%
    dplyr::select(nest, site, species, fdate, nest_age, obs_int, i, j, k, field_fate, fate, final_fate, cfate, cam_fate, status, year )%>%
    summarize(status = list(status),
              across(where(is.integer), last), # now they are all chr
              across(where(is.numeric), last),
              across(where(is.character), last) # summarize already goes rowwise
    ) %>%
    rowwise() %>%
    mutate_if(is.list, ~paste(unlist(.), collapse = '|'))

  }

  cat("Make sure you've selected the correct values:\n\n")
  # cat("\nSpecies:\n" )
  print(table(ndGLM$species))
  # cat("\nSite:\n")
  print(table(ndGLM$site))
  # cat("\nYear:\n")
  print(table(ndGLM$year))
  cat("\nHow many NAs are there in camera fate?\n", sum(is.na(ndGLM$cfate)), "\n")
  cat("\nAnd in nest age?\n", sum(is.na(ndGLM$nest_age)), "\n")

  return(ndGLM)
}
```



#### add field fate function
```{r include=FALSE}
ff <- function(nData){
    cat("*** adding field fate category ***\n")
  cat("old final_fate category:\n")
  table(nData$final_fate)
  nData <- nData %>%
    mutate(field_fate = final_fate) %>%
    mutate(final_fate = coalesce(cam_fate, field_fate )) 
  cat("new final_fate category:\n")
  table(nData$final_fate)
  cat("new field_fate category:\n")
  table(nData$field_fate)
  
  nData$fdate <- nData$k
}
```

##*
------------------------------------------------------------------------

## 1. DATA

### a. Data settings: handling U-H/U-F values, etc

View the code to see the settings for this run.

```{r data-settings, echo=FALSE}

# old_data = TRUE
old_data = FALSE

# if(TRUE){
if(FALSE){
  UHisH = TRUE
  UFisF = TRUE
} else {
  UHisH = FALSE
  UFisF = FALSE
}

# feb = TRUE
feb = FALSE

addFieldFate = FALSE

grouped = TRUE

plots1 = FALSE
# plots2 = TRUE

# compare = TRUE
compare = FALSE

# debug = TRUE
debug = FALSE

# missing_diag = TRUE
missing_diag = FALSE

# separation = TRUE
separation = FALSE

# cam_str <- c("Y", "y", "Y*") # including all cams seems to make delta AIC smaller
cam_str <- c("Y", "y", "Y*", "Y.") # including all cams seems to make delta AIC smaller
# cam_str <- c("Y", "y", "Y*", "Y?")
# cam_str <- c("Y", "y")

sites_sel <- c("RUTE", "RUTW")

spp_sel <- c("LETE", "CONI")
# 
# # mget gives you a named list if you give it object names as strings!
# settings <- mget(c("old_data","UHisH", "UFisF", "feb", "addFieldFate", 
#                    "compare",  "debug", "grouped", "missing_diag", "separation",
#                    "cam_str", "sites_sel", "spp_sel"))
# 
# cat("SETTINGS:")
# print(settings)

```


### b. Load cleaned data:

To run python code need reticulate package.

```{r load-data, echo=FALSE}

# if(FALSE){
if(old_data){
  filename <- paste0(homeDir,"nest_data/nest_data_cleaned_0227_1740_.csv")
  addFieldFate = TRUE
  grouped      = FALSE
  compare      = FALSE
} else {
  # filename <- read_file(paste0(homeDir,"filename_cleaned.txt"))
  # filename <- read_file(paste0(homeDir,"nest_data/nest_data_grouped_0805_1225_edit.csv"))
  # filename <- paste0(homeDir,"nest_data/nest_data_grouped_0805_1225_edit3.csv")
  filename <- paste0(homeDir,read_file(paste0(homeDir, "nest_data/import_name.txt")))
}
# if(debug) cat("importing from:",filename,"\n\n")
cat("importing from:",filename,"\n\n")
# nData <- read_csv(filename)[-1]
nData <- read_csv(filename)

```

### c. Filter data and specify which columns to use for variables

Can use the feb values, but remember different nests were also included

```{r choose-var-values, echo=TRUE}
if(old_data){
  # cat("using old data")
  nData$fdate <- nData$k
  ff(nData) # add a field fate column
} else {
  nData$fdate <- nData$final_obs_date
  nData$final_fate <- nData$final_fate2
  # nData$field_fate <- nData$field_fate2
  nData$field_fate <- nData$field_fate3
  if(feb==TRUE){
    # cat("using february data")
    nData$obs_int <- nData$final_obs_int_feb
    nData$nest_age <- nData$nest_age_feb
    nData$cam_fate   <- nData$cam_fate_feb
  } else  {
    # cat("using regular data")
    # nData$obs_int <- nData$final_obs_int
    nData$obs_int <- nData$final_obs_int2
    nData$nest_age <- nData$nest_age1 # nest age based on actual obs date
    # nData$nest_age <- nData$nest_age2 # nest age based on hatch date
    nData$cam_fate   <- nData$cam_fate2
  }
}
# cat("Nest age values:\n")
# table(nData$nest_age)
```


```{r filter-data}
nd <- nData %>%
  filter(nest!=20365) %>% # found on hatch day
  filter( nest!=20259) %>% # NA for final_obs_int
  # mutate(field_fate = ifelse(nest==10235,"H",field_fate)) %>%
  # filter_dat(all_cam=all_cam, debug=T, grouped=T)
  # filter_dat(all_cam=all_cam, debug=debug, grouped=grouped)
  filter_dat1(cam_vect=cam_str, debug=debug, grouped=grouped, # filters for cam nests by default
             # spp=c("LETE", "CONI"), sites_sel=c("RUTE", "RUTW"))
             # spp=spp_sel, sites_sel=sites_sel)
             spp=spp_sel, sites=sites_sel)

```

How many NAs should there be in (camera) nest fate?

2021: 2
2020: 5
2019: 6

and nest age (of the remaining nests)?

2021: 13
2020: 1
2019: 2





```{r UHF-values, eval=FALSE, include=FALSE}
#### d. Decide how to deal with U-H and U-F values
# 
# See notes. I guess most 2020 nests were assumed to have hatched if they reached the estimated hatch date with no signs of predation? 
# But 20264 and 424 were already 2 days past est hatch on penultimate visit (and still had eggs); well past it on final. 
nd %>% filter(fate == 8) %>% select(nest, field_fate, cam_fate, fate, cfate)
nd %>% filter(field_fate %in% c("U-H","U-F", "U-A", "U-D")) %>% 
  select(nest, field_fate, cam_fate, fate, cfate)
```


```{r UHF-values2, echo=FALSE}
if(UHisH == FALSE){
  # makeU <- c(10235,10206,20260,30421,30932,30950)
  # makeU <- c(20260,20264,20424,30932,30950)
  # makeU <- c(30932,30950)
  # makeU <- c(20260,20322,30932,30934,30950,10258)
  # makeU <- c(20260,20322,30932,30934,30950,10258)
  makeU <- c(20260,20322,30932,30950,10258)
  # makeU <- c(10206,20260,30932,30950, 10240, 10242, 30917)
  # makeU <- c(10206,20260,30932,30950, 30917)
  cat("make U:", makeU)
  # makeU <- c(10225,20260,30932,30950)
  makeA <- c(30934)
  # makeA <- c(NA)
  makeF <- c(10242,10240)
  # makeA <- c(20322)
  # makeU <- c()
  makeH <- c(
    # 10127,10206,20218,20251,20263,20264,20266,20400,20405,20424,20460,30421, 30917,30938, 10235
    10127,20218,20251,20263,20266,20400,20405,20460,30421,30938, 10235, 20264, 20424,30917, 10206
    # 10127,10206,20218,20251,20263,20266,20400,20405,20460,30421,30917,30938,10235
    )
  # makeH <- c(10127,20218,20251,20263,20264,20266,20400,20405,20424,20460,30421,30938)
  cat("make H:", makeH)
  # makeH <- c(10127,10206,20218,20251,20263,20264,20266,20400,20405,20424,20460,30938,10235,20260,30421,30932)
  
  nd <- nd %>%
    mutate(fate = case_when(nest %in% makeU ~ 7,
                            nest %in% makeH ~ 1,
                            nest %in% makeA ~ 4,
                            nest %in% makeF ~ 0,
                            .default = fate))
  # nd %>% filter(fate == 8) %>% select(nest)
  nd %>% filter(field_fate %in% c("U-H", "U-A", "U-F", "U-D")) %>% select(nest, field_fate, cam_fate, fate, cfate)
  # nd %>% filter(nest %in% makeU) %>% select(fate, field_fate, final_fate)
  # nd %>% filter(nest %in% makeH) %>% select(fate, field_fate, final_fate)
  # nd %>% filter(nest %in% makeA) %>% select(fate, field_fate, final_fate)
                # camera     == "Y")
}
if(UHisH == TRUE){
  nd$fate[nd$fate==8]=1
}
# nd %>% filter(field_fate %in% c("U-F", "U-A", "U-D")) %>% select(nest, site, species, year, fdate, nest_age, fate, cfate, final_fate)
```

### e.  Add the response vars:

```{r add-response, echo=TRUE}
# ndGLM1 <- as.data.frame(add_vars(nd, debug=T))
ndGLM1 <- as.data.frame(add_vars(nd,
                                 # UHisH = UHisH,
                                 # UFisF =UFisF,
                                 debug=T))
# ndGLM1 <- ndGLM1 %>% select(nest, status, species, field_fate, cam_fate, final_fate, fate_date, fdate, nest_age, obs_int, how_mis, HF_mis, misclass, is_u, hatchfail, c_hatchfail, fate, cfate)
ndGLM1 <- ndGLM1 %>% select(nest, species, field_fate, cam_fate, final_fate, estHD, k_adj, fdate, nest_age, obs_int, how_mis, HF_mis, misclass, is_u, hatchfail, c_hatchfail, fate, cfate)
if(TRUE){
# if(FALSE){
  ndGLM1 %>% select(nest, species, field_fate, cam_fate, fate, cfate, hatchfail, c_hatchfail, HF_mis, is_u) %>% write.csv(paste0("fates",now,".csv"))
}

print_vars(ndGLM1)

```


------------------------------------------------------------------------
##*
------------------------------------------------------------------------

## 2. DIAGNOSTICS  

I moved some of these to fate_GLM_extras; can run them as a child

### a. Specify the data and variables to use

```{r names-1, eval=FALSE, include=FALSE}
# This is mostly for naming files in an informative way.

datName = "ndGLM1"
# datName = "ndGLM_"
dat = get(datName)

prVars <- c("species", "cam_fate", "obs_int", "nest_age", "fdate")
if(UHisH == TRUE & UFisF == TRUE){
  uVar <- "UHFisHF" 
}else{
  uVar <- ""
}

fname <- paste("nest_data/",datName, uVar, now, ".csv", sep="_")
write.csv(ndGLM1, fname)
# number of fate categories:
# fVar <- paste0("-",nfate,"fates")
```



```{r, child=if(missing_diag | separation) 'diagnostics.Rmd'}

```

```{r, child = if(plots1) 'fate_GLM_plots_tables.Rmd'}

```




##*
------------------------------------------------------------------------

## 3. PREPARE DATA FOR MODEL

### a. Look at/edit individual nests or groups of nests (OPTIONAL)

```{r examine-full-data, eval=FALSE, include=FALSE}
nestNum <- 30959
as.vector(ndGLM1[ndGLM1$nest==nestNum,])

ndGLM1$nest_age[ndGLM1$nest==30959] = 20

ndGLM1$fate_date[ndGLM1$nest %in% justFDate]
# ndGLM1[2,]
```



### b. Edit the data again to remove rows missing camera fate:

Remove the rows missing camera fate, which is a categorical var

Also, examine the missing values.

```{r remove-NA-fate}
ndGLM_miss1 <- dat_miss(ndGLM1) # moved this elsewhere because it is used there
# ndGLM1$obs_int[ndGLM1$obs_int>12] = 10

ndGLM_red <- ndGLM1[!is.na(ndGLM1$cam_fate),]
ndGLM_red <- ndGLM_red[ndGLM_red$cam_fate!="U",]
ndGLM_red$nest[is.na(ndGLM_red$misclass)] 
ndGLM_red$misclass[is.na(ndGLM_red$misclass)] = 0 

ndGLM_miss <- dat_miss(ndGLM_red)
```


### c. Edit and refactor the data:

This creaes the dataset to be used for the imputation

```{r set-types}
# ndGLM_miss <- dat_miss(ndGLM1)

ndGLM_red <- ndGLM_red %>%
  set_var_types() %>%
  # refactor(num_fate=4) %>%
  # refactor(num_fate=6) %>%
  mutate(mclass = misclass == 1,
         isu    = is_u == 1) %>%
  mutate(across(c(isu, mclass), as.factor))

# ndGLM_red$species <- relevel(ndGLM_red$species, ref="LETE")

print_vars(ndGLM_red)
```


```{r fate-cat}
nfate=6
ndGLM_ <- ndGLM_red %>%
  refactor(num_fate=nfate) 
levels(ndGLM_$cam_fate)
  
ndGLM_ %>% sapply(function(x) sum(is.na(x)))
var <- "nest_age"
stillMissing <- ndGLM_$nest[which(is.na(ndGLM_[[var]]))]


# ndGLM4 <- ndGLM_red %>%
#   refactor(num_fate=4) 
#   
# ndGLM3 <- ndGLM_red %>%
#   refactor(num_fate=3) 
```

### f. Compare dataframes  *optional* :

The old one didn't have the same columns; need to add some...

- add field_fate and change final_fate

Maybe better comparison after removing the unknown fate nests

```{r, child=if(compare) 'compare.Rmd'}

```
##*
------------------------------------------------------------------------

## 4. VISUALIZE DATA AFTER REMOVING NAs AND EDITING

### a. Specify the name of the data being used so the file outputs are named accordingly.

```{r names-2}
# datName <- "ndGLM_feb_cc"
# datName <- "ndGLM_cc"
datName <- "ndGLM_"
dat     <- get(datName)
# are U-H and U-fF treated as H and F, respectively?
if(UHisH == TRUE & UFisF == TRUE){
  uVar <- "UHFisHF" 
}else{
  uVar <- ""
}
# number of fate categories:
fVar <- paste0("-",nfate,"fates")

# this was to create data to use in the package:
# fn <- paste0("C:/Users/sarah/Dropbox/Models/nestGLM/","nestDat.csv" )
# write.csv(dat,file=fn)
```


### b. Examine data - Frequency tables:

```{r frtab2, echo=TRUE}
# tabb <- fr_tab(ndGLM4)
# tabbb <- fr_tab(ndGLM6)
# datName <- "ndGLM_feb_cc"
# tabbbb <- fr_tab(ndGLM_unscl_cc, vars="misclass")
# suff <- paste0("_ndGLMcc_UHisH_UFisF-","")
# suff <- paste0("_ndGLMcc")

suff <- paste0("_",datName,"_",uVar, fVar)
# tabbbb <- fr_tab(ndGLM_cc, vars="HF_mis",suffix = suff)
tabbbb <- fr_tab(dat, vars="HF_mis",suffix = suff)
# why does the complete cases dataframe have missing values for HF_mis?
knitr::include_graphics(paste0("analysis/",tabbbb), 
                        dpi=(1300/6)) # dpi setting = only thing that works
```


### c. Create more histograms:

Choose x-axis limits and bin width:

```{r plot-params2, echo=FALSE}
# brLabels <- c(0,2,4,6,8,10)
# dat <- ndGLM_unscl_cc
varss <- c("nest_age", "obs_int", "fdate")
cat("max values:\n")
# sapply(varss, function(x) max(ndGLM_cc[[x]], na.rm=TRUE))
sapply(varss, function(x) max(dat[[x]], na.rm=TRUE))
cat("\nand suggested bin width:\n")
# freedman diaconis rule for bin width
# fdBins <- sapply(varss, 
# sapply(varss,  function(x) 2* ( (IQR(dat[[x]])) / (length(dat)^(1/3)) ) )
sapply(varss,  
       # function(x) 2*((IQR(ndGLM_unscl_cc[[x]])) / (length(ndGLM_unscl_cc)^(1/3))) # length here is # columns
       function(x) 2*((IQR(dat[[x]], na.rm = TRUE)) / (length(dat[[x]])^(1/3)))
       )
```


```{r isu-plot2}
# hist(ndGLM_unscl_cc$nest_age, breaks="FD")
catPlotU <- plot_predictors(resp="is_u",
                     dat=dat,
                     vars = c("nest_age", "obs_int", "fdate"),
                     filTit    = "Nest Fate",
                     filLabs   = c("Classifiable\nin Field", 
                                   "Not Classifiable\nin Field"), 
                     filColors = c("#88CCEE", "#AA4499"),
                     # filColors = c("green", "#AA4499"),
                     xLabs     = c("Nest Age (Days)", 
                                   "Final Interval (Days)",
                                   "Day of Season"),
                     yLab      = "Count",
                     # xMaxVect = c(32, 10, 120),
                     # xMaxVect = c(32, 8, 120),
                     xMaxVect = c(32, 11, 120),
                     binWidthVect = c(3, 1, 12),
                     # suffix="UHisH_UFisF"
                     suffix=paste0(datName, uVar, fVar)
                     )#,
                     # br    = brLabels)
                     # brLabs    = brLabels)
# fname <- paste0("catplot",)
# ggsave("catplot_isu_NAremoved.svg",
#        plot=catPlotU,
#        device="svg",
#        width=24,
#        height=8,
#        units="cm"
#        )
```


```{r HFmis-plot2}
resp <- "HF_mis"
# resp <- "misclass"
catPlotMis <- plot_predictors(resp   = resp,
                    dat  = dat,
                    vars      = c("nest_age", "obs_int", "fdate"),
                    filTit    = "Nest Fate",
                    filLabs   = c("Correctly\nClassified", "Incorrectly\nClassified"),
                    filColors = c("#44AA99", "#EE7733"),
                    xLabs     = c("Nest Age (Days)", 
                                  "Final Interval (Days)",
                                  "Day of Season"),
                    yLab      = "Count",
                     # xMaxVect = c(32, 10, 120),
                     xMaxVect = c(32, 11, 120),
                     binWidthVect = c(3, 1, 12),
                     suffix=paste0(datName, uVar, fVar)
                    )
                    # suffix="UHisH_UFisF")#,
# 
# ggsave(sprintf("catplot_%s_NAremoved.svg", resp),
#        plot=catPlotMis,
#        device="svg",
#        width=24,
#        height=8,
#        units="cm"
#         )
# resp <- NULL
```


### d. Create more scatterplots:
```{r}
# names(pairList)
# pairList <- combn(predictors, m=2, simplify=F)
# spc <- 
pairList <- combn(prList, m=2, simplify=F)
plList <- lapply(pairList, function(x){
  # ggplot(data=dat, aes(x=get(x[1]), y=get(x[2])) ) +
  ggplot(data=dat, aes(x=get(x[[1]]), y=get(x[[2]])) ) +
    geom_point() +
    geom_smooth(method=lm) +
    # ggpmisc::stat_poly_eq() +
    xlab(names(x)[1]) +
    ylab(names(x)[2]) +
    # ggtitle("Correlation Plots - NA removed")+
    # ggpubr::stat_cor( geom="label", label.x.npc = "middle", label.y.npc = "top") #+
    ggpubr::stat_cor( geom="label", label.y.npc = "top", size=6, face="bold") +
    theme_classic() +
    theme(axis.text = element_text(size=14),
        axis.title = element_text(size=16), # can't do margins for x and y axis titles at once
        axis.title.y = element_text(margin=margin(r=5)),
        axis.title.x = element_text(margin=margin(t=5))) +
        # plot.margin=margin(c(0.3,1,0.3,0.1), "cm")
    # theme( plot.margin=unit(c(1,0.5,1,0.5), "cm") ) # margins for 3-column arrangment
    theme( plot.margin=unit(c(0.5,1,0.5,1), "cm") ) # margins for 3-row arrangement
    # theme(panel.background = element_rect(fill="lightgray", alpha=0.5))
  })
# dsgn <- "AB
#          C#"
# pl <- patchwork::wrap_plots(plList)
pl <- patchwork::wrap_plots(plList,
                            ncol=2,
                            nrow=2)
                            # design=dsgn)
# add plot margin after assembly?
# pl <- pl + theme( plot.margin=margin(c(1,1,1,0), "cm"))
# ggsave(filename=paste0("corrPlot", now, ".svg"))
pl

now = format(Sys.time(), "_%m%d_%H%M_")

fname <- paste0(homeDir, "figures/corr_plot_cc_", now, ".svg")
# ggsave(fname, plot=pl, width=9, height=3)
ggsave(fname, plot=pl, width=10, height=10)
```



```{r correlation-plots-2, eval=FALSE, include=FALSE}
library("PerformanceAnalytics")
cormat <- dat |> 
  select(nest_age, obs_int, fdate) |>
  data.matrix() |>
  chart.Correlation(histogram=T)
```

### Separation & missing data diagnostics (optional)
```{r, child=if(missing_diag | separation) 'diagnostics.Rmd'}

```
### More tables:

```{r eval=FALSE, include=FALSE}
# fail <- c("S","F","Hu","D","A")
fail <- c(0,2:6)
corr_fate <- ndGLM_ %>% 
  # filter(HF_mis==1) %>%
  filter(misclass==1) %>%
  mutate(
    correction = case_when(
      fate == 7 & cfate %in% fail ~ "U to F",
      fate == 7 & cfate == 1 ~ "U to H",
      fate == 1 & cfate %in% fail ~ "H to F",
      fate %in% fail & cfate == 1 ~ "F to H",
      fate %in% fail & fate != cfate ~ "cause of fail"
    )) %>% select(nest, species, field_fate, cam_fate, correction)

cat("nests marked unknown that actually failed:\n", 
    corr_fate$nest[corr_fate$correction=="U to F"])
cat("\n\nnests marked unknown that actually hatched:\n",
    corr_fate$nest[corr_fate$correction=="U to H"])
cat("\n\nnests marked failed that actually hatched:\n",
    corr_fate$nest[corr_fate$correction=="F to H"])
cat("\n\nnests marked hatched that actually failed:\n",
    corr_fate$nest[corr_fate$correction=="H to F"])
    # correction = case_when(
    #   field_fate == "U" & cam_fate == "H" ~ "U to H",
    #   field_fate == "U" & cam_fate %in% fail  ~ "U to F",
    #   field_fate %in% fail & cam_fate == "H" ~ "F to H",
    #   field_fate == "H" & cam_fate %in% fail ~ "H to F"
    # )
  # )
  
```

Estimate bias for hatch date:

```{r eval=FALSE, include=FALSE}
est_hatch <- ndGLM_$estHD[ndGLM_$cam_fate=="H"]
names(est_hatch) <- as.character(ndGLM_$nest[ndGLM_$cam_fate=="H"])

true_hatch <- ndGLM_$k_adj[ndGLM_$cam_fate=="H"]
names(true_hatch) <- as.character(ndGLM_$nest[ndGLM_$cam_fate=="H"])
plot(x=est_hatch, y=true_hatch)
# mtr <- caret::confusionMatrix(est_hatch, true_hatch)
# as.character(ndGLM_$nest[ndGLM_$cam_fate=="H"])
# 
# est_hatch <- ndGLM_ %>%
#   filter(!is.na())
```


##*
------------------------------------------------------------------------

## 5. RUN THE MODELS
### a. Create the complete cases dataframe



```{r rem-NA, include=FALSE}
### Choose which data to use (how many nest fate categories)
# ndGLM_unscl <- ndGLM 
# ndGLM_unscl <- ndGLM6  %>% select(
# ndGLM_unscl <- ndGLM_  %>% select(s
# ndGLM_ <- ndGLM_ 
  # set_var_types() %>%
  # refactor(num_fate=4)


# ndGLM_unscl_cc <- ndGLM_unscl %>% # I don't know why this isn't working
ndGLM_cc <- ndGLM_  %>%
  select(
    nest, is_u, HF_mis, misclass, species, cam_fate, nest_age,
    fdate, obs_int
) %>% # I don't know why this isn't working
  remove_na(allNA = ndGLM_miss)

print_vars(ndGLM_cc)
# ndGLM_unscl_cc %>% sapply(function(x) sum(is.na(x)))
```

### b. Create scaled dataframe:

```{r scale-df, echo=TRUE}
# ndGLM_scl <- ndGLM1 %>%
ndGLM_scl <- ndGLM_ %>%
  # set_var_types() %>%
  # refactor(num_fate=4)%>%
  # scale( center=TRUE, scale=FALSE)
  mutate(across(predictors, function(x) as.numeric(scale(x,scale=F)))) #%>%
ndGLM_scl_cc <- ndGLM_scl %>% remove_na(allNA = ndGLM_miss)
```


### c. Define the models that will be compared:

THey aren't ONLY the models I initially had hypotheses about, BUT we are also not fishing through every possible model. 

```{r formulas, echo=FALSE}
# resp="is_u"
modList <- c()
modList <- c(
  "~ species + nest_age + fdate + cam_fate + obs_int",
  "~ 1",
  "~ species + nest_age + fdate + obs_int",
  # "~ species + cam_fate * nest_age + fdate + obs_int",
  # "~ species * cam_fate + nest_age + fdate + obs_int",
  "~ species * obs_int + cam_fate + nest_age + fdate ",
  # "~ species + cam_fate + fdate + obs_int * nest_age ",
  # "~ species + nest_age + fdate + obs_int * cam_fate",
  "~ nest_age * species + fdate + obs_int + cam_fate",
  # "~ species + cam_fate + nest_age + obs_int * fdate"
  # "~ species * fdate + cam_fate + nest_age + obs_int"
  # "~ species + nest_age + cam_fate + obs_int",
  # "~ species * nest_age + cam_fate + obs_int",
  # "~ species + cam_fate * nest_age + obs_int",
  # "~ species * obs_int + cam_fate + nest_age ",
  # "~ species + cam_fate + obs_int * nest_age ",
  # "~ species + nest_age + obs_int * cam_fate",
  "~ species + nest_age + cam_fate + fdate",
  "~ nest_age + cam_fate + fdate + obs_int",
  "~ nest_age + cam_fate + fdate"
  # "~ species + nest_age + cam_fate",
  # "~ species * nest_age + cam_fate",
  # "~ species + nest_age * cam_fate",
  # "~ species + nest_age ",
  # "~ species * nest_age ",
  # "~ nest_age "
  
)

# glmFit <- glm(formula="isu ~ species * nest_age + fdate + obs_int + cam_fate", 
#               family = binomial(), 
#               data = ndGLM_unscl_cc)
```

### d. Define the data and vars that will be used:
Put the name of the dataframe so it can be used in the file naming.
Also lets you choose the response variable for question 2 (HF_mis or misclass) and the method to use for the logistic regression

```{r mod-data}

# datName      <- "ndGLM_cc"
datName      <- "ndGLM_scl_cc"
# datNameImp   <- "ndGLM_"
datNameImp   <- "ndGLM_scl"
# datName      <- "ndGLM_feb_cc"
# datNameImp   <- "ndGLM_2"
resp1   <- "is_u"
resp2   <- "HF_mis"
# resp2   <- "misclass"
# met     <- "glm.fit"
# met     <- "jeffreys"
met     <- "brglm2"

# impRes <- ndGLM_red %>%
imppDat <- get(datNameImp)
cat("imputation using this data:", datNameImp)
```


------------------------------------------------------------------------
##*
------------------------------------------------------------------------

## QUESTION 1: What affects whether nest fate is classifiable from field evidence?

AKA is there field evidence or not

Think about which interactions make sense in answering this question

-   Response: is_u

Interaction models

-   What interactions make biological sense?

species \* age \| species \* obsint \| species \* fate age \* obsint \|
age \* fate \| obsint \* date \| obsint \* fate

Can I actually predict the magnitude/direction of the interaction for
them?

*Even if the model numbers are not sequential, will still work (see code
later on)*

brglmFit does the Firth penalization by default Firth's logistic
regression is best for explanatory; adds bias to predictions

### Analysis (complete cases)

Make sure there are no warnings.

#### Run the normal analysis:

```{r q1}
question <- "Was nest fate classifiable in the field?"

# dat <- parse(datName) # this one appears to be for files
dat <- get(datName)
mods <- list()

cat(question)
cat("\n\nData used:", datName)
cat("\n\nNumber of fate categories:", length(levels(dat$cam_fate)))
cat("\n\nRESPONSE VAR:",resp1)
# mods <- run_models(dataMod=dat, resp="is_u", modlist=modList)
# cat("\n\nclassifiable / not classifiable in field")
# table(ndGLM_unscl_cc$is_u)

# mods <- run_models(dataMod=dat, resp="is_u", modlist=modList, met="brglm2", iter=500000)
# mods <- run_models(dataMod=dat, resp="is_u", modlist=modList, met="jeffreys")
# mods <- run_models(dataMod=dat, resp=resp1, met="glm.fit", modlist=modList)
mods <- run_models(dataMod=dat, resp=resp1, met=met, modlist=modList)
# write.csv(ndGLM_cc, "nestdata2_.csv")
# sjPlot::plot_model(mods[[5]], type="int")
```

#### Create and save the AIC table

```{r q1-aic, echo=FALSE}
# fname <- mods %>% bic_mod() %>% save_tab()
# suffix = "_unscl_cc_q1"
# suffix = paste0("_unscl_cc_q1_",nfate,"fates")
suffix = paste0("-",datName,"-q1-",uVar,fVar)
# suffix = "_scl_cc_q1"
aicTab <- unname(mods) %>% aic_mod()
fname <- aicTab %>% save_tab(suffix=suffix, rtf=TRUE)
cat("creating AIC table; filename =",fname)

knitr::include_graphics(paste0("analysis/",fname), 
                        dpi=(1300/6)) # dpi setting = only thing that works
# MuMIn::model.sel(mods)
# modified_mods <- lapply(mods, MASS::glm.convert)
# AICcmodavg::aictab(cand.set=modified_mods)
```

#### Create and save the regression table for the best model

For the main effects model, I get a separation warning again D:

```{r q1-regtab, echo=FALSE}
# first, find the number of the best model
# modnum = 13# manually enter number for top model
# get all the model names:
modNames <- as.list(modnames(mods)) # list of models in the order they were specified
topMod = aicTab$`_data`$`__GT_ROWNAME_PRIVATE__`[1]
cat("top model:", topMod)
secTopMod = aicTab$`_data`$`__GT_ROWNAME_PRIVATE__`[2]
cat("second best model:", secTopMod)
cat("delta AIC of second best model:", aicTab$`_data`$dAICc[2])
modnum = which(modNames == topMod)
modnum2 = which(modNames == secTopMod)
cat("creating regression table for top model, model number", modnum, "; model formula:", paste(mods[[modnum]]$formula))
regrTab <- tabRegr(modNum=modnum, 
                   mods=mods, 
                   resp=resp1,
                   debug=T,
                   suffix=paste0(datName,"q1_",uVar,fVar))
knitr::include_graphics(paste0("analysis/",regrTab), 
                        dpi=(1300/6)) # dpi setting = only thing that works
```

#### Plot the top model:

```{r q1-plot, eval=FALSE, include=FALSE}
intPlot <- sjPlot::plot_model(
  mods[[modnum]], 
  type="int",
  title="Predicted probabilities of marking nest fate \"unknown\" in the field",
  axis.title=c("FINAL_OBS_INTERVAL","MARKED_UNKNOWN"),
  legend.title="TRUE_FATE"
  
  ) + scale_color_manual(
    values=c("H"="skyblue2", "D"="green3", "A"="red3", "F"="purple2"),
    labels=c("H"="Hatched", "D"="Depredated", "A"="Abandoned", "F"="Failed (other)")
  )
intPlot
# plogis(predict(fitted_model)) should convert the log-odds output of the model
# to a probability; use predict(fitted_model, type="response") to see prob
# of your data values.. can also calculate probs by hand if you want

dataMod$probfull <- plogis(predict(mods[[1]]))
dataMod$prob5 <- plogis(predict(mods[[5]]))  

y = "probfull"
x1 = "nest_age"
x2 = "species"

ggplot(dataMod, aes(x=.data[[x1]], y=.data[[y]])) +
  geom_point(aes(color=.data[[x2]])) + 
  geom_abline()
```

#### Odds ratios

```{r q1-OR, eval=FALSE, include=FALSE}
# knitr::include_graphics(filename2,
#                         dpi=(1300/6)) # dpi setting = only thing that works
oddrat <- mods |> 
  discard(is.null) |>
  odd_rat()
oddrat
```

When we don't impute the NAs, it's a complete cases analysis (all NA
rows removed automatically) BUT I need to be the one to remove the rows,
or I'll be comparing models with different sample sizes


### USING THE IMPUTED DATASETS:

The imputed datasets are stored in one object of class "mids"

The default for the mice package is to run all of the imputed datasets
(20, in this case) through your model and pool the results

-   Since I have many models, I looped through them and applied this
    default approach first

```{r q1-impute}
impRes <- imppDat %>%
  select(nest, nest_age, obs_int, cam_fate, fdate, species, HF_mis, misclass, is_u) %>%
  # runImpMods(.,modList=modList,resp="is_u")
  runImpMods(.,modList=modList,regMethod = "brglm2",resp=resp1)
# summary(impRes)
# impRes
# lapply(impRes, summary)
  fname <- paste0(datName,"impAIC_q1_",uVar,fVar)
aicImp <- aicImpMods(impModPool = impRes,modList = modList,filePrefix = fname)
# impTab <- impModTab(impModPool = impRes,modList = modList)
# aicImp
# knitr::include_graphics(paste0("analysis/",fname), 
knitr::include_graphics(aicImp, 
                        dpi=(1300/6)) # dpi setting = only thing that works
```




```{r q1-impute-2}
# this works:
impDat1 <- get(datNameImp)
impDat  <- mice::mice(impDat1, seed=613, m=100, printFlag=FALSE)
fit <- with(impDat, glm(as.formula(paste(resp, modList[[5]])), family=binomial, method=brglm2::brglmFit)) 
# pass results to tbl_regression before pooling, and it will handle pooling + tidying:
vars=c('species', 'nest_age', 'obs_int', 'cam_fate', 'fdate')
varNames=c('SPECIES', 'NEST_AGE', 'FINAL_INTERVAL', 'TRUE_FATE', 'END_DATE')
vnames = as.list(varNames)    
names(vnames) <- vars
# tabOR <- gtsummary::tbl_regression(pool.fit, label=vnames, exponentiate=TRUE)
summ.fit <- gtsummary::tbl_regression(fit, label=vnames, exponentiate=TRUE)
summ.fit
fn <- sprintf("_q1_reg_imp_%s_%s.rtf", datNameImp, now)
summ.fit %>%
  gtsummary::as_gt() %>%
  gt::gtsave( filename=fn, path="analysis/" )

```


##*
------------------------------------------------------------------------

## QUESTION 2: How do the predictor vars affect classification accuracy?

Response: HF_mis were nests correctly marked hatched/failed, or not

*NOTE* MAYBE should be recast as "was nest hatch misclassified?" so that unknowns that were actually hatched count as misclassified but unknowns that were actually failed don't?

### Analysis (complete cases )

#### Specify & run the analysis

```{r q2, echo=TRUE}
question <- "Was nest fate classified correctly in the field?"
cat(question)
dat <- get(datName)
mods <- list()
# cat("\n\nNumber of fate categories:", length(levels(ndGLM_2_cc$cam_fate)))
cat("\n\nData used:", datName)
cat("\n\nNumber of fate categories:", length(levels(dat$cam_fate)))
# mods <- run_models(dataMod=datList[[i]], resp="is_u", modlist=modList)
cat("\n\nRESPONSE VAR:",resp2,"\n\nMODELS:\n")
# mods <- run_models(dataMod=dat, resp=resp, met="logistf", modlist=modList)
# mods <- run_models(dataMod=dat, resp=resp, met="jeffreys", modlist=modList)
# mods <- run_models(dataMod=dat, resp=resp2, met="glm.fit", modlist=modList)
mods <- run_models(dataMod=dat, resp=resp2, met=met, modlist=modList)
# mods <- run_models(dataMod=dat, resp=resp, met="brglm2", modlist=modList)
# intPlot <- 
sjPlot::set_theme(
  base=theme_classic()
  
)
sjPlot::plot_model(mods[[5]], type="int") +
  labs(x="Nest age (days)", y="Predicted probability \nof misclassification", title="Interaction Plot for Species and Nest Age")

# j+
  # theme_classic()


#+
 # scale_fill_manual(values = species,
  #                  labels=c("Common\nNighthawk",
   #                          "Least\nTern"))
# intPlot
```


```{r echo=TRUE}
```

#### Create and save the AIC table

```{r q2-aic, echo=FALSE}
# fname <- mods %>% bic_mod() %>% save_tab()
# suffix = paste0("_unscl_cc_q2_", nfate, "_fates")
# suffix = paste0("-",datName,"-q2-", nfate, "fates")
suffix = paste0("-",datName,"-q2-", uVar,fVar)
# suffix = "_scl_cc_q1"

aicTab <- unname(mods) %>% aic_mod()
fname <- aicTab %>% save_tab(suffix=suffix, rtf=TRUE)
cat("creating AIC table; filename =",fname)

knitr::include_graphics(paste0("analysis/",fname),
                        dpi=(1300/6)) # dpi setting = only thing that works

```

#### Create and save the regression table for the best model

```{r q2-regtab, echo=TRUE}
# first, find the number of the best model
# modnum = 13# manually enter number for top model
# get all the model names:
modNames <- as.list(modnames(mods)) # list of models in the order they were specified
# c <- confset(cand.set=mods, modnames=modNames, method='raw')
# 
# while(aWeight < 0.95){
#   
#
topMod = aicTab$`_data`$`__GT_ROWNAME_PRIVATE__`[1]
cat("top model:", topMod)
secTopMod = aicTab$`_data`$`__GT_ROWNAME_PRIVATE__`[2]
cat("second best model:", secTopMod)
cat("delta AIC of second best model:", aicTab$`_data`$dAICc[2])
modnum = which(modNames == topMod)
modnum2 = which(modNames == secTopMod)
cat("creating regression table for top model, model number", modnum, "; model formula:", paste(mods[[modnum]]$formula) )

regrTab <- tabRegr(modNum=modnum,
                   mods=mods,
                   resp=resp2,
                   debug=T,
                   # suffix =paste0("q2_",nfate,"fates"))
                   suffix =paste0(datName,"q2_",uVar,fVar))
knitr::include_graphics(paste0("analysis/",regrTab), 
                        dpi=(1300/6)) # dpi setting = only thing that works
# confSet <- length(which(cumsum(aicTab$`_data`$weight)<0.95))
# confSet <- which(cumsum(aicTab$`_data`$weight)<0.95) # this doesn't get the last one unless it sums to exactly 0.95
```


```{r q2-regtab2, eval=FALSE, include=FALSE}
newNames=c('SPECIES', 'NEST_AGE', 'FINAL_INTERVAL', 'TRUE_FATE', 'END_DATE')
vars=c('species', 'nest_age', 'obs_int', 'cam_fate', 'fdate')
vnames <- as.list(newNames)
names(vnames) <- vars
  
                    
tabOR <- gtsummary::tbl_regression(mods[[modnum]],
                          label = vnames,
                          # label= list(
                          #   # resp~paste(r), # can't label response var
                          #             species~"SPECIES",
                          #             nest_age~"NEST_AGE",
                          #             obs_int~"FINAL_INTERVAL",
                          #             cam_fate~"TRUE_FATE",
                          #             fdate~"END_DATE"),
                          exponentiate=T)

```

### USING THE IMPUTED DATASETS:

```{r q2-impute, echo=TRUE}
# impDat <- ndGLM_imp   
fam <- binomial
# met <- "brglmFit"
# resp <- "HF_mis"
# resp <- "misclass"

cat("imputation using this data:", datNameImp)

impRes <- imppDat %>%
  select(nest, nest_age, obs_int, cam_fate, fdate, species, HF_mis, misclass, is_u) %>%
  runImpMods(.,modList=modList,regMethod = "brglm2",resp=resp2)
  # runImpMods(.,modList=modList,regMethod = "glm.fit",resp=resp2)
# impRes
# lapply(impRes, summary)

fname <- paste0(datName,"impAIC_q2_",uVar,fVar)
# aicImp <- aicImpMods(impRes, fname)
aicImp <- aicImpMods(impModPool = impRes,modList = modList,filePrefix = fname)
# aicImp <- aicImpMods(impRes, "impAIC_q2_")
# aicImp
knitr::include_graphics(aicImp, 
                        dpi=(1300/6)) # dpi setting = only thing that works
```


```{r q2-impute-2, echo=TRUE}
# summary(pool(fit)) doesn't give the results the website claims it does, but only when you call model fit from a list?
# this works:
impDat1 <- get(datNameImp)
impDat  <- mice::mice(impDat1, seed=613, m=100, printFlag=FALSE)
fit <- with(impDat, glm(as.formula(paste(resp2, modList[[5]])), family=binomial, method=brglm2::brglmFit)) 
# pass results to tbl_regression before pooling, and it will handle pooling + tidying:
vars=c('species', 'nest_age', 'obs_int', 'cam_fate', 'fdate')
varNames=c('SPECIES', 'NEST_AGE', 'FINAL_INTERVAL', 'TRUE_FATE', 'END_DATE')
vnames = as.list(varNames)    
names(vnames) <- vars
# tabOR <- gtsummary::tbl_regression(pool.fit, label=vnames, exponentiate=TRUE)
summ.fit <- gtsummary::tbl_regression(fit, label=vnames, exponentiate=TRUE)
summ.fit
fn <- sprintf("_q2_reg_imp_%s_%s.rtf", datNameImp, now)
summ.fit %>%
  gtsummary::as_gt() %>%
  gt::gtsave( filename=fn, path="analysis/" )
```


```{r q2-impute-3, eval=FALSE, include=FALSE}
# you can still also look at pooled results:
pool.fit <- mice::pool(fit)
summary(pool.fit)

# these don't:
mod_num <- 5
fit <- mods[[5]]
summary(fit)
fit_imp <- impRes[[mod_num]]$pooled
fit_imp
summary(fit_imp)
reg_sum <- summary(impRes[[5]]$pooled)
reg_sum[,2]

pool.OR <- exp(cbind(reg_sum[,1]))
# impRes[[5]]$pooled %>%
#   select(term, estimate, )

```


------------------------------------------------------------------------
### end
------------------------------------------------------------------------