---
title: "rmark_format"
author: "Sarah Bolinger"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nestGLM)
homeDir <- "C:/Users/sarah/Dropbox/nest_models/"
```

```{r eval=FALSE, include=FALSE}
filename <- paste0(homeDir, "nest_data/nest_data_cleaned_0805_1955_.csv")
nestData2 <- read_csv(filename)
```

Starting with grouped data:

```{r}

# filename <- paste0(homeDir, "nest_data/nest_data_cleaned_0805_1955_.csv")
filename <- paste0(homeDir,read_file(paste0(homeDir, "nest_data/import_name.txt")))
cat("importing from:",filename,"\n\n")
nestData2 <- read_csv(filename)

nestData2 <- nestData2 %>%
  mutate(
    cam_fate = cam_fate2, 
    field_fate = field_fate2,
    final_fate = final_fate2, 
    fdate      = final_obs_date,
    obs_int    = final_obs_int2,
    nest_age   = nest_age1
  )
table(nestData2$field_fate)
```


```{r}
cam_vect <- c("Y", "y", "Y*", "Y.") # including all cams seems to make delta AIC smaller
nestData1 <- nestData2 %>%
   mutate( final_fate = case_match(field_fate,
                                   "H"   ~ 1,
                                   "F"   ~ 0,
                                   "D"   ~ 2,
                                   "S"   ~ 3,
                                   "A"   ~ 4,
                                   "Hu"  ~ 5,
                                   "Ca"  ~ 6,
                                   "U"   ~ 7,
                                   "U?"  ~ 7,
                                   "U-H" ~ 8
           ),

           cam_fate = case_match(cam_fate,
                                 "H"  ~ 1,
                                 "F"  ~ 0,
                                 "D"  ~ 2,
                                 "S"  ~ 3,
                                 "A"  ~ 4,
                                 "Hu" ~ 5,
                                 "Ca" ~ 6,
                                 "U"  ~ 7
           ),
           camera = ifelse(camera %in% cam_vect, TRUE, FALSE)
   )
```



## Formatting for DSR models ------------------------------------------------
###
Let's start with the DSR models, which require less formatting. This
data will become 2 datasets per DSR model: one w/ camera fates included
and one without.

We can remove nests with unknown final fate--all nests with (original) fates of
"U" "U?" and "U-H"--which includes nests that were not tracked to final fate
and nests whose fate was not clear based on the field data. 

We will remove all nests with fates 7 and 8. As before with "NA" fate nests, we 
will record the nest numbers so we know which nests are being excluded, as well
as how many.

Or make fate 8 == hatch??


```{r eval=FALSE, include=FALSE}

n <- nestData1$nest

ijk    <- nestData1 %>%
  filter(!is.na(k)) %>%
  mutate(
    # ff=grep("[:digit:]+(?=\\|)", )
    ff=str_extract( obs_dates,"[0-9]+(?=\\|)"),
    la = stringi::stri_extract_last_regex(obs_dates, "[0-9]+(?=\\|)"),
    # la = str_extract(nestData1$obs_dates)
    lc = stringi::stri_extract_last_regex(obs_dates, "(?<=\\|)[0-9]+")
  )
```


Unknown nests - do we keep them as unknown or move 8 and 9 to hatch and fail, respectively?
Conservative estimate and less conservative estimate?
Codes:
                                 "U"   ~ 7,
                                 "U?"  ~ 7,
                                 "U-H" ~ 8,
                                 "U-F" ~ 9,
                                 "U-A" ~ 9,
                                 "U-D" ~ 9
                                 
                                 


```{r eval=FALSE, include=FALSE}
totNest <- unique(nestData1$nest)
# unknown <- nestData[nestData$final_fate %in% c(7,8) ,]
nestData1$cam_fate[nestData1$cam_fate == 7] = NA
```

Conservative estimate:

```{r eval=FALSE, include=FALSE}
unknown <- nestData1[nestData1$final_fate %in% c(7:9)  & is.na(nestData1$cam_fate),] 
uNest  <- unique(unknown$nest)
```

Less conservative estimate:

```{r eval=FALSE, include=FALSE}
unknown1 <- nestData1[nestData1$final_fate == 7 & is.na(nestData1$cam_fate),] 
uNest1  <- unique(unknown1$nest)
#uNests  # view all nests with unknown fate
```


```{r eval=FALSE, include=FALSE}
# kNA     <- which(is.na(nestData$k)) # which rows
kNAnest <- unique(nestData1$nest[(which(is.na(nestData1$k)))])

# MORE CONSERVATIVE
nestRm  <- union(uNest, kNAnest) # which nests being removed
nestRm                            # view them
# LESS CONSERVATIVE
nestRm1 <- union(uNest1, kNAnest)
nestRm1

# nests that violate RMark assumptions:
bad     <- union(wrong,wrong2)
bad     <- union(bad, wrong3)
```


```{r eval=FALSE, include=FALSE}
# ordered <- (ijk$k > ijk$i) & (ijk$k > ijk$j)
ordered <- (ijk$k > ijk$i)
ordered2 <- (ijk$k >= ijk$j)

# which(ordered==FALSE)
nestData1$nest[ordered==FALSE]
nestData1$nest[ordered2==FALSE]
nestData1$nest[nestData1$k < nestData1$j]
# checkNests <- nestData1 %>% group_by(nest) %>%
#   #summarize(final = last(status),
#   mutate(final_fate = as.character(final_fate)) %>% # col types must match
#   mutate(status_ = ifelse(last_obs == T, final_fate, status)) %>% # final status = fate
# #checkNests <- checkNests %>% group_by(nest) %>%
#   summarize(
#             final_day = max(season_day),
#             k=last(k),
#             status= list(status_), #%>%
#             final_obs = last(status_),
#             final_fate = last(final_fate)
#   ) 

# checkNests$remove <- checkNests$nest %in% nestRm
# goodNests <- checkNests |>
#   # filter(final_fate %in% c(0:6), !is.na(k)) %>%
#   filter(remove == FALSE) |>
#   filter( lengths(status) > 1) 
# # after summarizing, status_ doesn't exist anymore
#   #filter(final == final_fate)
```

The full set of MARK nests:
This excludes nests that both have no final fate and no cam fate
Equivalent to the "camera" dataset except we haven't changed final fate to cam fate yet
MORE CONSERVATIVE
df.duplicated returns a df containing all duplicate rows, including the first instance
so if two different rows appear more than once, all are included
but DOESN'T include the index of the row in the original df...
if you run duplicated (base R function) with fromLast=T AND then again with fromLast=F, should get all rows including the first instance
(ex: 

```{r eval=FALSE, include=FALSE}
dat <- data.frame(x1 = c(1, 1, 2, 2, 4),
                  x2 = c(1, 1, 2, 2, 6),
                  x3 = c(2, 2, 3, 3, 6),
                  x4 = c(1, 1, 2, 2, 4),
                  x5 = c(1, 1, 2, 2, 6))
dups <- misty::df.duplicated(.,data=dat)

```

remember: rows, not columns (x1-x5 are columns)

```{r echo=TRUE}
MARKnest <- nestData1 |> 
  # group_by(nest) |>
  mutate(final_fate = as.character(final_fate),
    ff=str_extract( obs_dates,"[0-9]+(?=\\|)"),
    la = stringi::stri_extract_last_regex(obs_dates, "[0-9]+(?=\\|)"),
    # la = str_extract(nestData1$obs_dates)
    lc = stringi::stri_extract_last_regex(obs_dates, "(?<=\\|)[0-9]+")
         # k      = ifelse(!is.na(cam_fate) & !is.na(fate_date),
         #                 fate_date,
         #                 k)
         ) |>
  # mutate(status_ = ifelse(last_obs == T, final_fate, status)) |>
  # mutate(remove = nest %in% nestRm) |>
  # mutate(check  = nest %in% bad) |>
  # filter(remove == FALSE) |>
  filter(k > i,
         species %in% c("CONI", "LETE"),
         site %in% c("RUTW", "RUTE")) |>
  select(nest, species, cam_fate, final_fate, i, ff, j, j_adj, la, k, k_adj, lc,
         site, year, cov_1m, cov_5m, prot, init_date, nest_age)
```





Check for duplicate observation histories (rows):

```{r eval=FALSE, include=FALSE}
# MARKnest0$dup <- duplicated(MARKnest)|duplicated(MARKnest, fromLast=T)
MARKnest$dup <- duplicated(MARKnest)|duplicated(MARKnest, fromLast=T)
which(MARKnest$dup == TRUE)
```

Make it MARK-compatible:
hatch is now 0, fail is 1

```{r echo=TRUE}
# if no duplicate rows (obs histories), continue with analysis

MARKnest <- MARKnest |>
  mutate(

    # status = ifelse(status == 1, 0, 1), # status is a list, doesn't work
    fate   = ifelse(final_fate==1,0,1),
    cfate  = ifelse(cam_fate==1,0,1),
    # n      = ifelse(dup==TRUE, T, 1)
    freq   = 1
  ) 

# MARKnest$j_adj[MARKnest$nest==20405] =94

  
```

Now, compare last checked vs k, etc.?

```{r}
# 
```

For the "camera" dataset, make last status cam_fate (if applicable); otherwise, keep it as final_fate
*NOTE* status isn't really relevant for MARK, but could be for other models...
K also changes because we know the actual last day of the nest for most of them
In cases where k > j after looking at cam footage, set j == the new k 

```{r echo=TRUE}
MARKnestCam <- MARKnest |>
  # select(nest,  site, cov_1m, cov_5m, prot, init_date,)
  mutate(
         # update = !is.na(cam_fate) & !is.na(fate_date) & fate == 0,
         fate   = ifelse(!is.na(cam_fate), cfate, fate), # replace with the one that's been transformed for RMark
         final_final_fate = ifelse(!is.na(cam_fate), cam_fate, final_fate),
         k      = ifelse(!is.na(k_adj), k_adj, k),
         j      = ifelse(!is.na(j_adj), j_adj, j)
  )|>
  filter(final_final_fate %in% c(0:6)) |>
  select(nest, site, species, i, ff, j, la, k, lc, fate, freq,
                  cov_1m, cov_5m, prot, init_date, nest_age)
```


```{r echo=TRUE}
MARKnestCam %>%
# MARKnestFld %>%
  filter(fate == 0) %>%
  filter(j != k) %>% 
  select(nest) %>%
  unlist(use.names=FALSE)
# table(MARKnest$final_fate)
# 

# MARKnestCam2 <- MARKnestCam |>
# MARKnestCam <- MARKnestCam |>
#   mutate(
#     # status = ifelse(last_obs == T & !is.na(cam_fate),
#                          # cam_fate,
#                          # status),
#          # k      = ifelse(camera == T & !is.na(fate_date),
#          # k      = ifelse(!is.na(cam_fate) & !is.na(fate_date) & fate == 0,
#          k      = ifelse(update==TRUE,
#                          fate_date,
#                          k),
#                          # fate_date,
#                          # k),
#          # j      = ifelse(!is.na(fate_date) & k==fate_date & fate == 0,
#          j      = ifelse(fate == 0,
#                          k,
#                          j),
#          # fate   = ifelse(!is.na(cam_fate), cfate, fate) # replace with the one that's been transformed for RMark
#          # ID     = paste("/*",nest,"*/" )
#          ) |>
#   select(nest, i, j, k, fate, freq, nocc, species, nest_age, final_fate, cam_fate)
```


```{r eval=FALSE, include=FALSE}
MARKnestFld <- MARKnest |>
  filter(final_fate %in% c(0:6)) |>
  select(nest, site, species, ff, i, la, j, lc, k, fate, freq,
                  cov_1m, cov_5m, prot, init_date, nest_age)
# 
# MARKnestFld$j[MARKnestFld$nest==20231] = 48
# MARKnestFld$j[MARKnestFld$nest==30935] = 81
# MARKnestFld$j[MARKnestFld$nest==10127] = 81
  # |>
  # select(nest, i, j, k, fate, freq, nocc, species, nest_age, final_fate, cam_fate)
```


```{r eval=FALSE, include=FALSE}
MARKnestFld %>% 
  filter(fate == 0) %>%
  filter(j != k) %>% 
  select(nest) %>%
  unlist(use.names=FALSE)
```

```{r eval=FALSE, include=FALSE}
# write.csv()
now = format(Sys.time(), "%m%d_%H%M_")
# MARKnest$bad <- 
# fname1 <- sprintf("model_data/ruth_rmark_cam_%s.csv", now)
# fname2 <- sprintf("model_data/ruth_rmark_fld_%s.csv", now)
fname1 <- sprintf("%s/model_data/ruth_rmark_cam_%s.csv", homeDir,now)
fname2 <- sprintf("%s/model_data/ruth_rmark_fld_%s.csv",homeDir, now)
fname1
fname2
write.csv(MARKnestCam, fname1)
write.csv(MARKnestFld, fname2)
```





Remember the nest fate codes:
                                 "H"   ~ 1, 
                                 "F"   ~ 0, 
                                 "D"   ~ 2,
                                 "S"   ~ 3,
                                 "A"   ~ 4,
                                 "Hu"  ~ 5,
                                 "Ca"  ~ 6,


Don't remove unknown fate nests until you split into field and camera

```{r eval=FALSE, include=FALSE}
# ijk     <- c(i,j,k)
# ndDSR   <- nestData %>% # something is setting status to 0 for every row
#   # mutate(status_ = ifelse(last_obs == T, final_fate, status)) %>%
#   mutate(status = ifelse(last_obs == T, final_fate, status)) %>%
  # seems to be !is.na(k)
  # also, k values are way off again...
  # group_by(nest) %>%
  # summarize(
  #           final_day = max(season_day),
  #           k=last(k),
  #           status= list(status_), #%>%
  #           final_obs = last(status_),
  #           final_fate = last(final_fate)
  # ) %>% 
  # 
  # filter(final_fate %in% c(0:6), !is.na(k))
  # mutate(status_ = ifelse(last_obs == T, final_fate, status)) %>%
  # filter(status_ %in% c(0:6)) %>% 
# cat("final fate frequency:\n")
# table(ndDSR$final_fate)
# cat("\n\nNests in DSR model:\n\n")
# unique(ndDSR$nest) # which nests are left?

```

### field vs. camera
Go ahead and remove nests with missing covariates? 
Or go thru and make sure i,j,k are correct for all nests?
I am honestly not sure what I was doing in this chunk:
(and then I split it up, too)

```{r eval=FALSE, include=FALSE}
# nestCam  <- unique(ndDSR$nest[!is.na(ndDSR$cam_fate)])
# camera nests left after removing k==NA AND filtering out U fate nests

n <- unique(nestData1$nest[nestData1$same_ID==0])

# ndDSRcam <- nestData %>%
ndDSR <- nestData1 %>%
#   # mutate(status = ifelse(last_obs == T & camera == T & !is.na(cam_fate), 
  filter(nest %in% n) %>%
#   # filter(!is.na(k)) %>% 
#   mutate(status = ifelse(last_obs == T & !is.na(cam_fate), 
#                          cam_fate,
#                          status),
#          k      = ifelse(camera == T & !is.na(fate_date),
#                          fate_date,
#                          k),
#          # final_fate = ifelse(final_fate %in% c(7:9) & !is.na(cam_fate),
#          #                     cam_fate,
#          #                     final_fate),
#          season_day = as.numeric(season_day))
# # for cam nests, replace final fate with camera fate
```

### When should NAs be removed?

```{r}
# # ndDSRcam1 <- ndDSRcam[ndDSRcam$cam_fate %in% c(0:6),]
# ndDSRcam1 <- ndDSRcam[ndDSRcam$final_fate %in% c(0:6),]
# # ndDSRcam1 <- ndDSRcam1[!is.na(ndDSRcam1$final_fate),] # REMOVE NAs
# ndDSRcam1 <- ndDSRcam1[!is.na(ndDSRcam1$k),] # REMOVE NAs
# ndDSRcam1 <- ndDSRcam1[!is.na(ndDSRcam1$i),] # REMOVE NAs
# ndDSRcam1 <- ndDSRcam1[!is.na(ndDSRcam1$j),] # REMOVE NAs
# ndDSRcam1 <- ndDSRcam1[!is.na(ndDSRcam1$nest_age),] # REMOVE NAs
```

```{r}
# ndDSRfield <- nestData %>%
#   filter(nest %in% n) %>%
#   filter(!is.na(k)) %>%
#   mutate(status = ifelse(last_obs == T & !is.na(cam_fate), 
#                          cam_fate,
#                          status),
#          k      = ifelse(camera == T & !is.na(fate_date),
#                          fate_date,
#                          k),
#          season_day = as.numeric(season_day))
# 
# ndDSRfield1 <- ndDSRfield[ndDSRfield$final_fate %in% c(0:6),]  
# ndDSRfield1 <- ndDSRfield1[!is.na(ndDSRfield1$final_fate),] # REMOVE NAs
# ndDSRfield1 <- ndDSRfield1[!is.na(ndDSRfield1$k),] # REMOVE NAs
# ndDSRfield1 <- ndDSRfield1[!is.na(ndDSRfield1$i),] # REMOVE NAs
# ndDSRfield1 <- ndDSRfield1[!is.na(ndDSRfield1$j),] # REMOVE NAs
# ndDSRfield1 <- ndDSRfield1[!is.na(ndDSRfield1$nest_age),] # REMOVE NAs

```

Camera-assisted data:
```{r eval=FALSE, include=FALSE}
n <- unique(nestData1$nest[nestData1$same_ID==0])
final_fate = ifelse(final_fate %in% c(7:9) & !is.na(cam_fate),
                             cam_fate,
                             final_fate)
```

Check that everything was transformed the way we expected:

```{r}
# good <- unique(ndDSR$nest[which( max(ndDSR$status) == ndDSR$final_fate )])

#   #
# bad <- good %>% 
#   filter(final_day != k)
# 
# alsoBad <- good %>%
#   filter(lengths(status)<2) # note function "lengths"
# 
# weirdNests <- good$nest[which(good$final_day != good$k)]
# 


```

### Program MARK 

If we want to use the data in Program MARK, we need the following:

-   nest ID

-   nest observation history

-   values for i (first found), j (last seen active), and k (last
    observed)

-   does any other nest have this exact history?

-   covariate values, if applicable

For hatched nests, j will often == k because the final observation is of
newly-hatched chicks.

```{r eval=FALSE, include=FALSE}
ndMARKfld <- ndDSRfield1 %>%                  # field data (no cameras) 
  #filter(camera == FALSE) %>% 
  mutate(status = ifelse(status == 1, 0, 1),
         fate   = ifelse(final_fate==1,0,1) )%>%  # in MARK, 0=alive, 1=dead
  group_by(nest, site, species) %>%
  # group_by(nest) %>%   
  # even when you group by nest and not the other 2, ii is wrong
  # select(nest, final_fate, fate, status, i, j, k, cov_5m, nest_age, season_day) %>%
  summarize(status = list(status), 
            i=min(season_day), # why does this get messed up for a few rows???
            # jj=ifelse(last(final_fate==1), max(season_day), nth_max(season_day, n=2)),
            j= eeptools::nth_max(season_day, n=2), # change for hatched nests later
            k=max(season_day),
            # ii=min(season_day), # why does this get messed up for a few rows???
            # # needed to make numeric
            # # jj=ifelse(last(final_fate==1), max(season_day), nth_max(season_day, n=2)),
            # jj= nth_max(season_day, n=2), # change for hatched nests later
            # kk=max(season_day),
            # i = max(i),
            # j = max(j),
            # k = max(k),
            fate = last(fate),
            cam_fate   = last(cam_fate),
            nest_age   = max(nest_age)
            # j=ifelse(final_fate==1, max(season_day), nth_max(season_day, n=2)))
            # across(where(is.integer), last),
            # across(where(is.numeric), last),
            # across(where(is.character), first)
  ) %>%
  mutate_if(is.list, ~paste(unlist(.), collapse = '|')) 
ndMARKfld$nocc <- max(ndDSRfield1$season_day)
```

For the data including the cameras, keep "fate_date" because that will become the new "k" (the camera lets us know exactly how long the nest survived during the final observation interval instead of guessing)

```{r eval=FALSE, include=FALSE}
ndMARKcam <- ndDSRcam1 %>%                  # field + camera data
  mutate(status = ifelse(status == 1, 0, 1),
         fate   = ifelse(final_fate==1,0,1) )%>%  # in MARK, 0=alive, 1=dead
  # group_by(nest, site, species) %>%   
  group_by(nest, site, species) %>%   

  summarize(status = list(status), 
            # ii=min(season_day), # why does this get messed up for a few rows???
            # # jj=ifelse(last(final_fate==1), max(season_day), nth_max(season_day, n=2)),
            # jj= nth_max(season_day, n=2), # change for hatched nests later
            # kk=max(season_day),
            i=min(season_day), # why does this get messed up for a few rows???
            # jj=ifelse(last(final_fate==1), max(season_day), nth_max(season_day, n=2)),
            j= eeptools::nth_max(season_day, n=2), # change for hatched nests later
            k=max(season_day),
            # i = max(i),
            # j = max(j),
            # k = max(k),
            fate = last(fate),
            cam_fate   = last(cam_fate),
            nest_age   = max(nest_age)
            # j=ifelse(final_fate==1, max(season_day), nth_max(season_day, n=2)))
            # across(where(is.integer), last),
            # across(where(is.numeric), last),
            # across(where(is.character), first)
  ) %>%
  
  # select(nest, site, species, status, i,ii, j,jj, k,kk, final_fate, fate, cov_5m, nest_age, cam_fate, season_day ) %>%
  # mutate(lastObs = ifelse(cam_fate == 1, 0, lastObs)) %>% # ???
  
  # mutate_if(is.list, ~paste(unlist(.), collapse = ',')) 
  mutate_if(is.list, ~paste(unlist(.), collapse = '|')) 
wrong_order <- which(ndMARKcam$i > ndMARKcam$k)
wo          <- ndMARKcam[wrong_order,] # ??? these are ones where ii > kk, not i>k
which(ndMARKcam$ii > ndMARKcam$kk)
ndMARKcam$nocc <- max(ndDSRcam1$season_day)

```

Now save the MARK data to csv:

```{r eval=FALSE, include=FALSE}
# now = "830_1826"
if(file.exists("model_data") == FALSE) dir.create("model_data")

filename <- paste0("model_data/MARK_data_field_",now,".csv")
write.csv(ndMARKfld, filename)

filename <- paste0("model_data/MARK_data_cam_",now,".csv")
write.csv(ndMARKcam, filename)
```

### Bayesian logistic exposure model

Unlike Program MARK, the Bayesian multinomial logistic DSR model allows us to include multiple causes of nest failure, like we coded for earlier. Now we can reformat the nest fates so that there are fewer categories, which should make DSR model interpretation easier.

(In reality, how many causes of failure can we include and still be able to interpret the model output? Do I have too many?)

The "cattle" category includes both nests that were destroyed by cattle
and nests that were abandoned because of cattle disturbance. We will
lump the cattle-destroyed nests in with human-destroyed nests, and
cattle-abandonment nests with all other abandoned nests. These are the
new categories:

0 - failed (unknown/unspecified) \| 1 - hatched 
2 - depredated \| 3 - storm-related (surge, flooding) 
4 - abandoned \| 5 - destroyed (human, cattle)

```{r eval=FALSE, include=FALSE}
# visually inspect nests with fate Ca and Hu in the Excel sheet to look for 
# notes about specific cause of failure and status of nest at last observation 
# (were there still eggs, but abandoned due to disturbance, or were eggs 
# destroyed?)

chNests <- ndDSR %>% 
  filter(final_fate %in% c(5,6) | cam_fate %in% c(5,6)) %>%
  mutate(nest = as.character(nest),  # data types must match to join 
         final_fate = as.character(final_fate)) %>%
  # mutate(notes = allData$NOTES) %>%
  group_by(nest) %>%
  summarize(final_fate = last(final_fate),
            cam_fate   = last(cam_fate),
            final_obs  = last(final_obs),
            status     = list(status)) 
# chNests <- chNests %>% left_join(allData, by = join_by(nest)) 
# join by both nest and final_fate to avoid duplicating final_fate
# except that seems to make NOTES == NA?
# chNests1 <- chNests %>% left_join(allData, by = join_by(nest, final_fate)) 
# notes <- read_delim("output/field_notes_0830_1438_.csv", 
notes <- read_csv("output/field_notes_0830_1438_.csv",
                  # col_names = c("nest", "notes"),
                  col_types = cols(.default="c"),
                  col_select= c(2:3)
)

names(notes) <- c("nest", "notes")

nfates <- table(ndDSR$final_fate)
ncfates <- table(ndDSR$cam_fate)

                  # col_select = c(starts_with("allData"))
                  # delim = " "
                  # )# only loading one column
# chNests1 <- chNests %>% left_join(allData, by = join_by(nest )) 
chNests1 <- chNests %>% left_join(notes, by = join_by(nest )) 
chNests1 <- chNests1 %>%  select(nest, status, cam_fate, final_fate, final_obs, notes)
# chNests1 <- chNests1 %>%  select(nest, status, cam_fate.x, final_fate.x, final_obs, NOTES)

dsKey <- c("destroyed", "crushed", "cracked", "trampled", "run over", "Ran over", "Stick broken")
abKey <- c("cold", "abandoned", "getting eaten by ants", "loose egg")
```

```{r}
# for(n in nrow(chNests1)) append(newF, str_extract(chNests1$NOTES[n], dsKey))
# for(n in 1:nrow(chNests1)) newF[[n]] <- str_extract(chNests1$NOTES[n], dsKey)
# newF2 <- list()
# for(n in 1:nrow(chNests1)) newF2[[n]] <- str_extract(chNests1$NOTES[n], abKey)

# newF <- coalesce(newF, newF2)
# newF <- 
# for(n in 1:nrow(chNests1)) {
#   newF[[n]] <- case_when(
#     !is.na(str_extract(chNests1$NOTES[n], dsKey)) ~ "Ds",
#     !is.na(str_extract(chNests1$NOTES[n], abKey)) ~ "A",
#     !is.na(str_extract(chNests1$NOTES[n], "tracks")) & chNests1$final_obs %in% dead ~ "Ds", 
#     !is.na(str_extract(chNests1$NOTES[n], "tracks")) & chNests1$final_obs %in% alive ~ "A",
#   ) 
# for(n in 1:nrow(chNests1)) {
#   newF[[n]] <- case_when(
#     all(!is.na(str_extract(chNests1$NOTES[n], dsKey))) ~ "Ds",
#     all(!is.na(str_extract(chNests1$NOTES[n], abKey))) ~ "A",
#     all(!is.na(str_extract(chNests1$NOTES[n], "tracks"))) & chNests1$final_obs %in% dead ~ "Ds",
#     all(!is.na(str_extract(chNests1$NOTES[n], "tracks"))) & chNests1$final_obs %in% alive ~ "A",
#   )}
# for(n in 1:nrow(chNests1)) {
#   # newF[[n]] <- case_when(
#   newF[n] <- case_when(
#     !all(is.na(str_extract(chNests1$NOTES[n], dsKey))) ~ "Ds",
#     !all(is.na(str_extract(chNests1$NOTES[n], abKey))) ~ "A",
#     !all(is.na(str_extract(chNests1$NOTES[n], c("track","print")))) & chNests1$final_obs %in% dead ~ "Ds",
#     !all(is.na(str_extract(chNests1$NOTES[n], c("track","print")))) & chNests1$final_obs %in% alive ~ "A",
#   )
# }
# chNests1[which(is.na(newF) == is.na(chNests1$NOTES)),]
# which((is.na(newF) == is.na(chNests1$NOTES))==F)
# notmatch <- which(newF != chNests1$final_fate.x)
# already accounted for NA, so this should be the ones w/ no useful info in notes
# otherwise the NAs in one list should match the locations of NAs in the other
# which(chNests1)
# chNests1$NOTES[1]
# newF[[11]] <- !anyNA(str_extract(chNests1$NOTES[11], dsKey))
# chNests1$new_f <- 
# for(n in 1:nrow(chNests1)){
#   chNests$newF <-
#     case_when(!is.na(str_extract(chNests1$NOTES[n], dsKey))~"Ds",
#               !is.na(str_extract(chNests1$NOTES[n], abKey))~"A",
#             TRUE                                        ~chNests$final_fate[n])
# }
# newF[[11]] <- str_extract(chNests1$NOTES[11], dsKey)
# for(n in 1:nrow(chNests1)) {
  # str_extract(chNests1$NOTES[n], dsKey)
# }
# chNests2 <- chNests1 %>%
#   mutate(new_fate = case_when(
#   ))
#     str_extract(NOTES, dsKey ) ~ "Ds",
#     str_extract(NOTES, abKey) ~ "A"))
#Caused by error in `str_extract()`:
# ! Can't recycle `string` (size 75) to match `pattern` (size 7).
# Backtrace:
# # chNests1$NOTES[!is.na(chNests1$NOTES)]
# # chNests1 <- chNests %>%  left_join(allData, by = join_by(nest)) 

# chNests$notes <- allData$NOTES[allData$nest %in% chNests$nest]
# chNests$notes <- allData$NOTES[allData$nest == chNests$nest]

# chNests <- unique(chNests$nest) %>%

  # mutate(notes = allData$NOTES[allData$nest %in% chNests$nest])
  # mutate(notes = allData$NOTES[allData$nest == chNests$nest])
# chNests <- chNests %>% mutate(notes = allData$NOTES[which()])
# chNests <- chNests %>% mutate(notes = allData$NOTES[which(allData$nest == nest)])
# chNests <- chNests %>% mutate(notes = allData$NOTES[which(allData$nest == chNests$nest)])

# notes   <- data$NOTES[data$nest %in% chNests$nest,]
# notes   <- allData$NOTES[nestData$nest %in% chNests$nest]
# notes   <- V

# write(notes, sprintf("output/Ca_Hu_notes_%s.txt", now))
# write("notes from Ca and Hu fate nests", sprintf("output/Ca_Hu_notes_%s.txt", now))
# for(n in chNests) k



```

Insert the nest numbers of nests whose fate needs to change to abandoned or destroyed below, and their fates will be converted accordingly:

```{r eval=FALSE, include=FALSE}
alive = c('H', '3C', '2C', '1C', '3E', '2E', '1E', 'BON', 'chick behavior', 'nest behavior', 'hatch', 'poops') 

dead  = c('F', "fail", "0E", "D", "W", "empty", "0e", "no activity", "coyote", "no chicks or parents", "nothing", "no activity")
```

```{r eval=FALSE, include=FALSE}
newF <- list() 

for(n in 1:nrow(chNests1)) {
  # newF[[n]] <- case_when(
  newF[n] <- case_when(
    !all(is.na(str_extract(chNests1$notes[n], dsKey))) ~ "Ds",
    !all(is.na(str_extract(chNests1$notes[n], abKey))) ~ "A",
    !all(is.na(str_extract(chNests1$notes[n], c("track","print")))) & chNests1$final_obs %in% dead ~ "Ds",
    !all(is.na(str_extract(chNests1$notes[n], c("track","print")))) & chNests1$final_obs %in% alive ~ "A",
    TRUE ~ NA
  )
}

which((is.na(newF) == is.na(chNests1$notes))==F)
newF[newF=="Ds"] <- 5
newF[newF=="A"]  <- 4
nest <- chNests1$nest

newnewF <- as.data.frame(cbind(nest, newF))

# newF <- data.frame(nest=nest, fate=newF) # interpreted as x and y values
# newF <- data.frame(nest=nest, fate=newF)
# ndDSR <- nestData %>% mutate(final_fate = ifelse())

# ndDSR <- nestData %>%
  # mutate(finalfate = modifyList(final_fate,newF))
  # mutate(finalfate = modify_if(final_fate %in% c("A", "Hu"), newF))
#Caused by error in `modify_if()`:
# ℹ In index: 1.
# Caused by error:
# ! `.p()` must return a single `TRUE` or `FALSE`, not NULL.
# ndDSR <- nestData %>%
  # mutate(finalfate = modifyList(final_fate,newF))
```


```{r}
# mutate(finalfate = modify_if(.p=final_fate %in% c("A", "Hu"), .f=final_fate = newF))
# ndDSR$newF = newF
# ndDSR$finalF <- ifelse(ndDSR$final_fate )

# which(ndDSR[ndDSR$nest == chNests1$nest],)
# which(ndDSR$nest == chNests1$nest),
# nests <- which(ndDSR$nest %in% chNests1$nest)
# nestindex <- 
# nestnums <- unique(ndDSR$nest[nests])
# nestnums <- unique(nests)


# ndDSR$finalf[nestindex] <- 
# for(n in 1:length(nestindex)) ndDSR$finalf[nestindex[n]] = newnewF$newF[n]
# for(n in 1:length(nestindex)) ifelse() ndDSR$finalf[nestindex[n]] = newnewF$newF[n]
# 
# x=1 
# for(n in 1:length(ndDSR)) {
#   
#   if(n %in% nestindex  & !is.na(newnewF$newF[n])){
#     
#     ndDSR$finalf = newnewF$newF[x]
#     x = x+1
#       
#   }
#   else{
#     
#     ndDSR$finalf = ndDSR$final_fate
#     
#   }
# }
#----------------------------------------------------------------------------
```
```{r}
# nestindex <- (ndDSR$nest %in% chNests1$nest)

# ndDSR <- ndDSR %>% group_by(nest) %>% summarize(final_fate = last(final_fate),
#                                                 i          = last(i),
#                                                 j          = last(j),
#                                                 k          = last(k),
#                                                 status     = list(status),
#                                                 finalf     = last(finalf))
```

```{r eval=FALSE, include=FALSE}
ndDSR$nestindex <- (ndDSR$nest %in% chNests1$nest) # index of C-H nests
nests     <- chNests1$nest                         # numbers of C-H nests
ndDSR$finalf <- vector(length = nrow(ndDSR))

ndDSR$finalf[nestindex] <- newnewF$newF

for(n in 1:nrow(ndDSR)){
  
  # if ndDSR$nestindex 
  index = nestindex[n]
  ndDSR$finalf[n] <- n
  
}
```

```{r eval=FALSE, include=FALSE}
for(n in 1:length(nests)){
  
  ndDSR$finalf[ndDSR$nest == nests[n]] = newnewF$newF[n]
  
}

ndDSR$finalf[ndDSR$finalf == FALSE] = NA
# ndDSR$finalf[is.na(ndDSR$finalf)] #= ndDSR$final_fate
# ndDSR$finalf <- ifelse(is.na(ndDSR$finalf),
                       # ndDSR$final_fate,
                       # ndDSR$finalf)
                       # 
                       # 
ndDSR1 <- ndDSR %>% mutate(finalf = ifelse(is.na(finalf),
                                           final_fate,
                                           finalf))
ndDSR1 <- ndDSR1 %>%
  filter(nestindex) %>% 
  group_by(nest) %>% 
  summarize(fate     = last(final_fate),
            last_status   = last(status),
            new_fate = last(as.character(finalf)),
            k        = last(k),
            ) # %>% 
  #mutate_if(is.list, ~paste(unlist(.), collapse = ',')) # can't do this after ungrouping

nd <- as.data.frame(ndDSR1)
nd$notes <- chNests1$notes
nd$final_obs <- chNests1$final_obs

write.csv(nd, sprintf("output/aband_cattle_%s.csv",now))


# for(n in 1:nrow(chNests1)){
  # 
# }
```

AND NOW DO IT FOR CAM NESTS! WOOOHOOOO

```{r eval=FALSE, include=FALSE}
# ndDSR$finalf[which(nestindex == T)] # this isn't the way to use indices
  
# # ndDSR2 <- ungroup(ndDSR)  
# x=1
# for(n in 1:nrow(ndDSR)) {
#   #browser()
#   if(n %in% nests){ # & !is.na(newnewF$newF[n])){
#     # ndDSR$finalf <- newnewF$newF
#     newfate  <- as.character(newnewF$newF[n])
#     ndDSR$finalf <- newfate
#     x = x+1
#     cat("n = ", n, "|| new fate value:", newfate,  "|| x value:", x, "\n")
#       
#   }
#   else{
#     
#     ndDSR$finalf = NA 
#     
#   }
# }
# 
#   ndDSR$finalf[nestindex]
# 
# ndDSR$finalf[7]
  # 
  # ndDSR$finalf = ifelse(n %in% nestindex & !is.na(newnewF$newF[n]), 
  #                       newnewF$newF[x], 
  #                       ndDSR$final_fate[n])
  # if(n %in% nestindex) x = x + 1
  
#}
# ndDSR$finalf[nestindex] <- newnewF
# ndDSR$finalf <- ifelse() 
# ndDSR$finalf <- ifelse()



# newNewF <- rbind(ndDSR$final_fate, newF=newF[ndDSR$final_fate])
# ndDSR <- ndDSR %>%
  # mutate(finalfate = modifyList(final_fate,newF))
  # mutate(finalfate = ifelse(final_fate %in% c("A", "Hu") & !is.na(newF),
                            # newF, 
                            # final_fate))
# 
# check <- ndDSR %>%
#   group_by(nest) %>%
#   summarize(final_fate = last(final_fate),
#             finalfate  = last(finalfate),
#             status     = list(status))
# 
# which(ndDSR$finalfate != ndDSR$final_fate)
# 
# table(ndDSR$final_fate)

# so I guess none of them changed? 

```
```{r}
# ab <- c()
# ds <- c()
# 
# ndDSR <- nestData %>% 
#   mutate(final_fate = case_when(
#     nest %in% ab & final_fate %in% c(5,6) ~ 4,
#     nest %in% ds & final_fate %in% c(5,6) ~ 5
#   ), 
#   cam_fate = case_when(
#     nest %in% ab & cam_fate %in% c(5,6) ~ 4,
#     nest %in% ds & cam_fate %in% c(5,6) ~ 5
#   ))
```

(Data formatting info from Darrah et al. 2018 supporting information app. S3)
Read in nest data, which contains one row per observation per nest and the 
following columns:##
Nest.ID : factor with unique codes for each nest
Interval: length of nest check (exposure) interval
Status: nest status at each nest check. 1 = active, 2 = #depredated, 3 =  
flooded, 4 = abandoned, 5 = unknown cause #of failure
Veg.Cover: numeric column with cover categories 0-3
Habitat: factor column with habitat types
Exclosed: numeric column with 0 = no exclosure and 1 = #exclosure
Nest.Initiation: numeric column with Julian day of nest #initiation
(end extract from Darrah et al. 2018)

The first thing the Darrah script does is make an equivalent to "same_ID", so
keep that column

For the camera + field dataset, ...
For the no-camera dataset, fates are as assigned in the field, and k =
the last day the nest was observed in the field (as in the MARK data).

```{r eval=FALSE, include=FALSE}

ndDSRcam <- ndDSR %>% 
  mutate(k      = fate_date, 
         status = ifelse(lastObs == T, cam_fate, status)) %>%
  select(nest, species, status, obs_int, i, j, k, cov_5m, nest_age, same_ID)

ndDSR <- ndDSR %>%
  filter(camera == FALSE) %>%
  select(nest, species, status, obs_int, i, j, k, cov_5m, nest_age, same_ID)
```

Record the data for the Bayesian DSR model to csv:

```{r eval=FALSE, include=FALSE}

if(file.exists("model_data") == FALSE) dir.create("model_data")

filename <- paste0("model_data/nest_data_DSR_", now, ".csv")
write.csv(ndDSR, filename)

filename <- paste0("model_data/nest_data_DSR_cam_",now,".csv")
write.csv(ndDSRcam, filename)

```

------------------------------------------------------------------------

### Nest Fate Misclassification GLM

Now, the data for the GLM. First, we will select only the cameras with
nests, because the response variable is fate misclassification
(difference between camera and field fate).

We then reduce back to one row per nest by condensing the observation
history to one cell,

```{r eval=FALSE, include=FALSE}
# filename <- "model_data/all_nest_data_GLM_0823_1555.csv"
# ndGLM <- read_csv()

nestData <- read_csv("nest_data/nest_data_cleaned_0830_722.csv",
                     col_types = cols(.default="c"))
now = format(Sys.time(), "%m%d_%H%M_")
```

### If not reading in from CSV:

```{r eval=FALSE, include=FALSE}
ndGLM <- nestData %>% 
  filter(camera == TRUE) %>% 
  group_by(nest, site, species) %>%   
  select(nest, site, species, cov_5m, fate_date, nest_age, obs_int, i, j, k, final_fate, cam_fate, status, year )%>%
  summarize(status = list(status), 
            across(where(is.integer), last),
            across(where(is.numeric), last),
            across(where(is.character), first)
  ) %>%
  mutate_if(is.list, ~paste(unlist(.), collapse = '|'))

table(ndGLM$species)
table(ndGLM$site)
table(ndGLM$year)
 
```

```{r eval=FALSE, include=FALSE}
howMis <- function(fate, cfate){
  case_when(
    #fate == 0                  & cfate %in% c(2,3,4,5,6)     ~ "F", 
    #fate == 0            & cfate == 1           ~ "M", # fail-unkn -> hatch
    #fate == 0            & cfate %in% c(1:6)    ~ "M", # fail-unkn -> other
    #fate == 7            & cfate %in% c(0:6)    ~ "N", # unknown -> other
    
    fate %in% c(0:6)  & cfate != fate        ~ "M", # fate    -> other 
    fate %in% c(7,8)  & cfate %in% c(0:6)    ~ "N", # unknown -> other
    fate %in% c(0:6)  & cfate == 7           ~ "U"  # unknown cam fate
  )
}
```

```{r eval=FALSE, include=FALSE}
ndGLM <- ndGLM %>% 
  mutate(hatchfail = case_when(
    final_fate %in% c(0, 2:6) ~ 0, # fail
    final_fate == 1           ~ 1, # hatch
    final_fate == 7           ~ 7,
    final_fate == 8           ~ 7,
    final_fate == NA          ~ 7 # MAKE SURE all of these are coding correctly
  ),
  c_hatchfail = case_when(
    cam_fate %in% c(0, 2:6) ~ 0,
    cam_fate == 1           ~ 1,
    cam_fate == 7           ~ 7,  # hopefully not many/any of either of these
    #cam_fate == NA          ~ 7   # this one doesn't work - oh duh
    is.na(cam_fate)         ~ 7
    # remove cam_fate == 7?
  )) %>%
  mutate(HF_mis = case_when(
    c_hatchfail == 7 | hatchfail == 7 ~NA,
    c_hatchfail == hatchfail ~ 0, # nest wasn't misclassified
    c_hatchfail != hatchfail ~ 1  # nest was misclassified
  )) %>%
  mutate(HF_mis = ifelse(c_hatchfail == 7, NA, HF_mis),
         HF     = case_when(
           hatchfail == 0 & c_hatchfail == 1 ~ 101,
           hatchfail == 1 & c_hatchfail == 0 ~ 110
         )) # camera H/F unknown
  
  
```

```{r eval=FALSE, include=FALSE}
ndGLM <- ndGLM %>% 
  mutate(misclass = case_when(
    cam_fate == 7 ~ NA,
    final_fate == cam_fate ~ 1, # nest wasn't misclassified
    final_fate != cam_fate ~ 0   # nest was misclassified
  ) ) %>%
  mutate(how_mis = 
           case_when(misclass==0                 ~ howMis(final_fate, cam_fate),
                     misclass==1 & final_fate==7 ~ "U", 
                     misclass==1 & final_fate!=7 ~ "C"))


hmNA <- ndGLM$nest[which(is.na(ndGLM$how_mis))]

fates <- ndGLM %>% 
  select(nest,final_fate,cam_fate, misclass, how_mis, hatchfail, c_hatchfail, HF_mis, nest_age, fate_date)
```

```{r eval=FALSE, include=FALSE}

ndGLM_ <- ndGLM
camFateNA    <- ndGLM_$nest[which(is.na(ndGLM_$cam_fate))]  # 44 total, now 30
fate_dateNA  <- ndGLM_$nest[which(is.na(ndGLM_$fate_date))] # 50 total, now 44
is.na <- union(camFateNA, fate_dateNA)

nest_ageNA   <- ndGLM_$nest[which(is.na(ndGLM_$nest_age))]  # 66 total, now 31
is.na <- union(is.na, nest_ageNA) # 72 total nests to exclude-that's almost half

wmNA  <- ndGLM_$nest[which(is.na(ndGLM_$HF_mis))] 
is.na <- union(is.na, wmNA)

numNA <- length(is.na)
```

```{r eval=FALSE, include=FALSE}

# if(file.exists("model_data") == FALSE) dir.create("model_data")

filename4 <- paste0("model_data/all_nest_data_GLM_", now, ".csv")
# will give error if "now" has not been created

write.csv(ndGLM_, filename4, row.names = FALSE)
```

# 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
